### 2017-05-09 rs_study/experiments/paper/paper.tex
paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Neuroimage-like layout
\documentclass[5p]{elsarticle}
% For kindle
%\documentclass[1p,12pt]{elsarticle}
%\usepackage{geometry}
%\geometry{a6paper,hmargin={.2cm,.2cm},vmargin={1cm,1cm}}
% End kindle
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{xfrac}
\usepackage{bm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{afterpage}
\usepackage{url}
\usepackage[breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage[table]{xcolor}
\usepackage{booktabs}  % For toprule
\usepackage{multirow}
%\usepackage{stfloats} % To have double-column floats at the bottom
% (without this, it {figure*}[b] is impossible

% Never place a float before its reference
%\usepackage{flafter}

% For review: line numbers
%\usepackage[pagewise]{lineno}
\usepackage[switch]{lineno}
\modulolinenumbers[5]

\bibliographystyle{model2-names.bst}\biboptions{authoryear}

\definecolor{deep_blue}{rgb}{0,.2,.5}
\definecolor{dark_blue}{rgb}{0,.15,.5}

\hypersetup{pdftex,  % needed for pdflatex
  breaklinks=true,  % so long urls are correctly broken across lines
  colorlinks=true,
  linkcolor=dark_blue,
  citecolor=deep_blue,
}

% Float parameters, for more full pages.
\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.6}	% require fuller float pages
%    % N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dbltopfraction}{.95}  % double page floats at the top
\renewcommand{\dblfloatpagefraction}{.6}
\setcounter{totalnumber}{4}
\setcounter{topnumber}{3}
\setcounter{dbltopnumber}{3}
\setcounter{bottomnumber}{2}

\def\B#1{\mathbf{#1}}
%\def\B#1{\bm{#1}}
\def\trans{^\mathsf{T}}
% A compact fraction
\def\slantfrac#1#2{\kern.1em^{#1}\kern-.1em/\kern-.1em_{#2}}
\newlength{\mylength}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For the final version: to output PDF figures from latex
\newif\iffinal
\finaltrue
%\finalfalse
\iffinal\else
\usepackage[tightpage,active]{preview}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modification tracking
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\colorlet{markercolor}{purple!50!black}
\newcommand{\ADDED}[1]{\textcolor{markercolor}{\uline{#1}}}
\newcommand{\DELETED}[1]{\textcolor{red}{\sout{#1}}}

% For highlighting changes for reviewer
\usepackage{MnSymbol}
\def\marker{%
    \vadjust{{%
	\llap{\smash{%
	    \color{purple}%
	    \scalebox{1.8}{$\filledmedtriangleright$}}\;}%
    }}\hspace*{-.1ex}%
}%
\def\hl#1{\textcolor{markercolor}{%
   \protect\marker%
  #1%
}}%

% Show the old version
%\renewcommand{\ADDED}[1]{}
%\renewcommand{\DELETED}[1]{#1}

% Show the new version
%\renewcommand{\ADDED}[1]{#1}
%\renewcommand{\DELETED}[1]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
% Show line numbers
%\linenumbers
%\linenumbersep 3pt\relax
%\renewcommand\linenumberfont{\normalfont\tiny\sffamily\color{black!50}}

\journal{NeuroImage}
\title{Towards a better predictive model of rest fMRI: benchmarks across
multiple phenotypes}

%\author[parietal,cea]{Ga\"el Varoquaux\corref{corresponding}}
\author[parietal,cea]{Kamalaker Dadi}

\cortext[corresponding]{Corresponding author}

\address[parietal]{Parietal project-team, INRIA Saclay-\^ile de France,
France}
\address[cea]{CEA/Neurospin b\^at 145, 91191 Gif-Sur-Yvette, France}

\begin{abstract}
%
%
\end{abstract}

\begin{keyword}
    rs-fMRI; functional connectivity; predictive modeling; phenotypes;
    classification
\end{keyword}

\maketitle%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\smash{\raisebox{20em}{{\sffamily\bfseries Comments and Controversies}}}%
\vspace*{-3em}%

\sloppy % Fed up with messed-up line breaks

% XXX: read other commentary paper, for instance the Frison one
% Q: how much should I be citing things

\section{Introduction}%

% Start positive

% Introduce cross-validation
% State the problem
% Explain what I do, and our conclusion

% XXX: TODO: announce the content of the paper

\section{Methods}

\subsection{Overview of the pipeline}
\autoref{fig:pipeline}  depicts  our  prediction  pipeline.  It  consists  of  four
steps: i) Definition  of  brain  regions  of  interest  (ROIs),
ii) Extraction  of  the  time  series  associated  with  these  ROIs,
iii) Estimation  of  FC  metrics  from  these  time  series,
iv) Connectivity-based classification of the phenotypic target.
\subsection{Definition of brain regions or networks}

\subsection{Parameterizing connectivity}

\subsection{Supervised learning: Classifiers}

\section{Experimental study}

\subsection{rs-fMRI Datasets}

\subsection{Data \& prediction task}
\subsection{Cross validation}

%\paragraph{Previous results: cross-validation on brain images}

\begin{figure*}[t]
    \setlength{\fboxsep}{0pt}%
    \begin{minipage}[T]{.26\paperwidth}
     \includegraphics[height=.28\paperwidth]{pipeline.pdf}%
     \llap{\raisebox{.265\paperwidth}{%
	\parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
	\hspace*{-.15ex}\,\hspace{-2ex}}}}}%
    \medskip
    \end{minipage}
    \caption{\textbf{Resting-state functional connectivity prediction pipeline}}

    {\bfseries\sffamily 1} -- Defining Brain ROIs: involves using three
    pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
    - Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
    methods - Linear decomposition models: Group Independent Component
    Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
    Clustering models: KMeans - Agglomerative with Ward criterion. For each
    data-driven method, we build the atlas on training data ($75\%$) on each
    split (n=100) and use this atlas for the consecutive step. 
    %
    {\bfseries\sffamily 2} -- Timeseries signal extraction: For each atlas or
    ROIs, from Step 1 are used in extracting subject specific timeseries signals.
    %
    {\bfseries\sffamily 3} -- Parameterizing functional connectivity between
    ROIs,  using  correlation,  partial  correlation  or  tangent  space
    embedding
    %
    {\bfseries\sffamily 4} -- Supervised learning: Classifiers, a classification
    model is built to predict groups with two linear classifiers, SVC ($\ell_{1}$ or
    $\ell_{2}$ penalization) and ridge regression ($\ell_{2}$ penalization).
    %
    Cross-validation for 100 splits with $75\%$ training set and remaining
    $25\%$ test is used in Step 4, classification setting and reported scores
    are Receiver Operating Characteristic and Area Under the Curve (ROC-AUC)
    \label{fig:pipeline}
\end{figure*}

%\paragraph{Spread out predictions in a public challenge}

%website\footnote{\url{https://www.kaggle.com/c/mlsp-2014-mri}}.
\section{Results}

%    \begin{tabular}{llccl}
%    \toprule
%    Dataset        &       atlas &          classifier &    measure &
%    Score \\
%	%strategy  &        size &    error bar &    error bar \\
%    \toprule
%    \multirow{8}{9ex}{ADNI} & AAL &  SVC{$\ell_{1}$} &  correlation & $0.64$ \\
%                            &           BASC &  Ridge &   Tangent &    $0.71$ \\
%                            & DictLearn &  SVC{$\ell_{2}$} &   Tangent & $0.75$ \\
%                        &          Harvard Oxford &  Ridge & Tangent &   $0.66$ \\
%                            & Group ICA & Ridge & Tangent & $0.75$ \\
%                  & KMeans & Ridge & Tangent & $0.75$ \\
%                 & Ward & Ridge & Tangent & $0.71$ \\
%    \midrule                                            
%    \multirow{8}{9ex}{} & 30 &   &  \\
%                  &         100 &   &    \\
%                  &         300 &   &    \\
%	          &        1000 &   &    \\
%    \bottomrule
%    \end{tabular}}
%
%    \centering
%    \caption{\textbf{Comparison of the atlas impact on prediction accuracy.}
%        Reported values are the mean of AUC over 100 iterations.
%        Best predictions are in bold.}
%     \label{tab:accuracy}
%     \begin{tabular}{ccccc}
%         & COBRE & ADNI & ACPI & ADNIDOD \\
%         \hline\\[-2mm]
%         AAL       & $.81$ & $.64$ & $.55$ & $\bf .71$ \\
%         BASC      & $.82$ & $0.71$ & $0.56$ & $0.67$ \\
%         DictLearn & $\bf{ 0.85}$ & $\bf 0.75$  & $\bf 0.57$ & $\bf 0.68$ \\
%         HO        & $0.72$ & $0.66$ & $0.57$ & $0.65$ \\
%         ICA       & $0.83$ & $\bf 0.75$ & $0.55$ & $0.67$ \\
%         K-Means   & $0.84$ & $\bf 0.75$ & $\bf 0.58$ & $0.68$ \\
%         Ward      & $0.84$ & $0.71$ & $0.55$ & $\bf 0.69$ \\
%     \end{tabular}
% \end{table}
 \subsection{Choice of classifier}

\begin{figure}
    \centerline{%
    \includegraphics[width=.8\linewidth]{impact_plot_classifier.pdf}%
    }%
    \caption[choice of classifier]{\textbf{Impact of classifier choices on
    prediction scores}
\label{fig:impact_classifier}}
\end{figure}

\subsection{Choice of connectivity parameterization}

\begin{figure}
    \centerline{%
    \includegraphics[width=\linewidth]{impact_plot_measure.pdf}%
    }%
    \caption[choice of classifier]{\textbf{Impact of connectivity
            parameterization method choices on prediction scores}
\label{fig:impact_connectivity}}
\end{figure}

\subsection{Choice of atlas methods: Either regions or networks}

\begin{figure}
    \centerline{%
    \includegraphics[width=\linewidth]{impact_plot_atlas.pdf}%
    }%
    \caption[choice of atlas]{\textbf{Impact of atlas choices
        on prediction scores}
    \label{fig:impact_atlas}}
\end{figure}

\paragraph{Effect of dimensionality: Brain regions}

\begin{figure}
    \centerline{%
	\includegraphics[width=\linewidth]{dot_plot_n_regions_suppressed_background.pdf}%
    }%
    \caption[]{\textbf{Effect of dimensionality: Choice of brain regions} {For
            each of four atlases (ICA, DictLearn, KMeans, BASC) driven with region
            extraction, we show the measure of effect on prediction scores obtained by
            removing the mean effect of group relatively over all
            cross-validation splits and datasets.

            What we obtain then, is the demeaned score for each split and for each
            dataset.

            Given that, we plot here: for each atlas, we took the average of
            calculated demeaned scores over all splits which is showed on y-axis
            as choice of vary in dimensionality as showed on x-axis.

            For each atlas, we then see the effect of each dataset (each unique color)
            by projecting an error bar plot with $95\%$ confidence interval on each
            averaged score shown as violin plot in gray color.

            Given the plots, we choose here the best dimensionality in ICA of
            $80$, and DictLearn of $60$, KMeans of $120$ and BASC of $122$.

            These references in finding an optimalilty dimensionalities are
            then used for further comparisons of choosing the best atlas
            method.}
    %
    \label{fig:effect_size_in_regions}
    }
\end{figure}

To understand better the choice of atlas defined with or without region
extraction as a function of vary in dimensionality, we chose to see the mean
effect on prediction scores overall the cross validation folds with respect to
four reference atlases (ICA, Dictionary Learning, KMeans and BASC) with
various dimensionalities. \autoref{fig:effect_size_in_regions} outlines to choose
between the optimal dimensionality for each atlas as a function of regions.

\paragraph{Effect of dimensionality: Brain networks/parcellations}
%
\begin{figure}
    \centerline{%
	\includegraphics[width=\linewidth]{dot_plot_parcellations_suppressed_background2.pdf}%
    }%
    \caption[]{\textbf{Effect of dimensionality: Choice of brain
        networks/parcellations} {Atlases based on networks: ICA, DictLearn,
            BASC whereas based on parcellations are KMeans and Ward. In total,
            we are comparing here five brain atlases each driven without
            region extraction.

            We show the measure of effect on prediction scores obtained by
            removing the mean effect of group relatively over all cross-validation
            splits and datasets.

            As demonstrated in \autoref{fig:effect_size_in_regions}, we show
            the same the demeaned score for each split and for each dataset
            but this time without region extraction.

            Given that, we plot here: for each atlas, we took the average of
            calculated demeaned scores over all splits which is showed on y-axis
            as choice of vary in dimensionality as showed on x-axis.

            For each atlas, we then see the effect of each dataset (each unique color)
            by projecting an error bar plot with $95\%$ confidence interval on each
            averaged score shown as violin plot in gray color.

            Given the plots, we choose here the best dimensionality in
            networks: ICA of $80$, and DictLearn of $60$, KMeans of $120$ and BASC
            of $122$ and Ward of $120$.

            These references in finding an optimalilty dimensionalities without
            region extraction are then used for further comparisons of choosing
            the best atlas method.}
    %
    \label{fig:effect_size_in_networks}
    }
\end{figure}

\paragraph{Which is better: Brain atlases with regions or without regions}
Given the outlining the choice of optimal dimensionality of brain atlases with
or without regions extracted as shown in \autoref{fig:effect_size_in_regions}
and \autoref{fig:effect_size_in_networks}, we compare them to see which is
better in prediction. Prediction using atlases build with regions or
using atlases build with networks. As shown in
\autoref{fig:regions_vs_nonregions}, and atlas GroupICA or ICA, predicting
using regions is better rather than using only networks. Whereas for
Dictionary Learning, prediction using regions is better and same even with
BASC atlases. Interesting, to see that BASC which is a pre-defined atlase
built on unseen resting state functional datasets is better with regions
rather than only networks. While we see the opposite with KMeans based atlas
prediction. With KMeans, using parcellations without regions or
inter-hemispheric separation is better for prediction tasks of resting state
fMRI.

\begin{figure}
    \centerline{%
	\includegraphics[width=\linewidth]{violin_plot_mean_score_region_extraction_ica_dict_kmeans.pdf}%
    }%
    \caption[regions vs non regions]{\textbf{Which is better for prediction: regions or
        without regions}
        For each atlas (ICA, DictLearn, KMeans and BASC), we show here the
        best setting for prediction by measuring its impact on prediction
        accuracy for each dataset.

        Each data point is a measure of impact on prediction accuracy. For
        each atlas, data point in unique color is a score obtained by averaging
        raw prediction scores grouped by three classifiers, three measures.
        Each unique color is referred to each of four datasets used to test
        the prediction.

        We then compare these data points using violin plots with or without
        region extraction. On x-axis is the impact on prediction and on y-axis
        is to differentiate between region extraction and no region extraction.

        From the observations, ICA atlas based prediction has better impact
        by extracting regions on the networks which is quite similarly
        observed with Online Dictionary Learning and BASC. But, KMeans has
        better impact when predicted using without region extraction meaning
        that parcellations based atlas.
    %
    \label{fig:regions_vs_nonregions}
    }
\end{figure}

\section{Supplementary material}

\begin{figure}
    \centerline{%
	\includegraphics[width=.8\linewidth]{n_regions_vs_dimensionality.pdf}%
    }%
    \caption{\textbf{Number of regions extracted with dimensionality}
    %
    %
    \label{fig:n_regions_dim}
    }
\end{figure}

\begin{table}[t]
    \begin{tabular}{llllrlll}
        \toprule
        & Atlas &    Classifier & Measure &  Dimensionality & Regions & 
        ROC\textunderscore AUC &  Dataset \\
        \midrule
        &  Online Dictionary Learning & SVC-$\ell{_2}$ & Tangent & 60 & yes &
        0.86\$\textbackslashpm\$0.06 &    COBRE \\
        & K-Means & Ridge & Tangent & 120 & no &
        0.76\$\textbackslashpm\$0.09 &
        ADNI \\
        &                            AAL &  SVM-\$\textbackslashell\_1\$ &
        Tangent &             116 &      no &  0.72\$\textbackslashpm\$0.08 &
        ADNIDOD \\
        &                        K-Means &  SVM-\$\textbackslashell\_2\$ &
        Partial \textbackslashn Correlation &             120 &      no &
        0.58\$\textbackslashpm\$0.08 &     ACPI \\
        &                            ICA &  SVM-\$\textbackslashell\_2\$ &
        Tangent &              80 &     yes &   0.7\$\textbackslashpm\$0.03 &
        ABIDE \\
        \bottomrule
    \end{tabular}
\end{table}
%\begin{figure}
%    \includegraphics[width=\linewidth]{figures/performance_vs_size_2.pdf}%
%    \caption{\textbf{Reported accuracy and sample size}
    %
%    The various plots show reported prediction accuracy as a
%    function of sample size for the studies in different the
%    reviews considered in \autoref{fig:sample_size}.
    %
%    The black line and grey area represent the $p=0.05$ threshold with a
%    binomial null model, which, as shown in the results section, is
%    likely to be optimistic.
    %
%    The lines are Lowess fit to the data: robust non-parametric local
%    regression.
    %
%    \label{fig:reported_accuracy}
%    }
%\end{figure}

\section{Conclusion:}

% Acquiring large quality datasets is intrinsically a challenge in
% neuroimaging, whether it is psychiatric or cognitive
% (repetition effects)

%%% Position with regards to papers

% Recall the power-failure paper. Stress that the problem that I report
% is not a failure of the predictive models, which is also a risk. 
% The intuitions that we gain from standard statistics do not carry over
% well: One difference with standard statistics (as in the power-failure paper)
% is that the effect size matter. On the opposite, in classification,
% only correct vs incorrect is counted, which is the power and the
% limitation of the methods

% The paper by poldrack 
%\cite{poldrack2016scanning}

% cite Braga-Neto, "Is cross-validation valid for small-sample
% microarray classification?" to underline that this has been seen in
% genomics

% Stress that the problem is not fixed by better classifiers (my sport)

% Say that I have myself been overly optimistic and confident in my
% results in the development of decoders, some of which have not
% reproduced \cite{michelsupervised} though the core mathematical
% intuitions were correct \cite{rena}

\subsection*{Acknowledgments}

Funded by NiConnect project (ANR-11-BINF-0004\_NiConnect) and CATI.

% references section

\small
%\bibliographystyle{elsarticle-num-names}
\bibliography{biblio}

%\appendix
%\renewcommand{\thefigure}{A\arabic{figure}}
%\setcounter{figure}{0}
%\renewcommand{\thetable}{A\arabic{table}}
%\setcounter{table}{0}

%\begin{figure}%
    %\center%
    %\includegraphics[width=.7\linewidth]{github_code/sem_vs_error.pdf}%
    %\medskip

%    {\small\sffamily%
%    \begin{tabular}{llrrr}
    %\toprule
%	CV        &       train &          SEM &    empirical \\
%	strategy  &        size &    error bar &    error bar \\
%    \toprule
%    \multirow{4}{9ex}{LOO} & 30 &  $\pm 13.8\%$ &  $\pm 18.9\%$ \\
%		&           100 &  $\pm 7.4\%$ &   $\pm 10.3\%$ \\
%	        &           300 &  $\pm 4.1\%$ &   $\pm  5.9\%$ \\
%		&          1000 &  $\pm 2.2\%$ &   $\pm  2.9\%$ \\
%    \midrule                                            
%    \multirow{4}{9ex}{50 splits,\\20\% test} & 30 &  $\pm 3.4\%$ & $\pm 15.3\%$ \\
%                  &         100 &  $\pm 2.0\%$ &   $\pm  8.1\%$ \\
%                  &         300 &  $\pm 1.1\%$ &   $\pm  4.1\%$ \\
%	          &        1000 &  $\pm 0.6\%$ &   $\pm  2.1\%$ \\
    %\bottomrule
%    \end{tabular}}
%    \caption{\textbf{}
%    \label{fig:error_vs_sem}}
%\end{figure}

%\begin{figure}[t]
%    \centerline{%
%     \includegraphics[width=.8\linewidth]{github_code/dimensionality_results.pdf}%
%     \llap{\raisebox{.72\linewidth}{%
%	\parbox{.86\linewidth}{\bfseries\sffamily Binomial\\law}}}%
%    }%
%
%    \caption{\textbf{Distribution of errors as given by a binomial law}
%    Different between the observation prediction error and the 
%    population value of the probability of error for different sample sizes.
%    The bar and whiskers indicate the median
%    and the 5\raisebox{.5ex}{\tiny th} and 95\raisebox{.5ex}{\tiny th}
%    percentile. 
%    \label{fig:binomial}}
%\end{figure}

\end{document}

### 2017-05-27 rs_study/experiments/paper/paper.tex
Paper + Prediction scores from AAL on ABIDE data

@@
 \usepackage{url}
+\usepackage{tabularx}
 \usepackage[breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
@@
 \usepackage{multirow}
+\usepackage{adjustbox}
+\usepackage{lipsum}
 %\usepackage{stfloats} % To have double-column floats at the bottom
@@
 %\author[parietal,cea]{Ga\"el Varoquaux\corref{corresponding}}
-\author[parietal,cea]{Kamalaker Dadi}
+\author[parietal,cea]{XXXXX}
 
@@
 \sloppy % Fed up with messed-up line breaks
-
-% XXX: read other commentary paper, for instance the Frison one
-% Q: how much should I be citing things
 
@@
 
-\begin{figure*}[t]
-    \setlength{\fboxsep}{0pt}%
-    \begin{minipage}[T]{.26\paperwidth}
-     \includegraphics[height=.28\paperwidth]{pipeline.pdf}%
-     \llap{\raisebox{.265\paperwidth}{%
-	\parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
-	\hspace*{-.15ex}\,\hspace{-2ex}}}}}%
-    \medskip
-    \end{minipage}
-    \caption{\textbf{Resting-state functional connectivity prediction pipeline}}
-
-    {\bfseries\sffamily 1} -- Defining Brain ROIs: involves using three
-    pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
-    - Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
-    methods - Linear decomposition models: Group Independent Component
-    Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
-    Clustering models: KMeans - Agglomerative with Ward criterion. For each
-    data-driven method, we build the atlas on training data ($75\%$) on each
-    split (n=100) and use this atlas for the consecutive step. 
+%begin{figure*}[t]
+%   \setlength{\fboxsep}{0pt}%
+%   \begin{minipage}[T]{.26\paperwidth}
+%    \includegraphics[height=.28\paperwidth]{pipeline.pdf}%
+%    \llap{\raisebox{.265\paperwidth}{%
+%   \parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
+%   \hspace*{-.15ex}\,\hspace{-2ex}}}}}%
+%   \medskip
+%   \end{minipage}
+%   \caption{\textbf{Resting-state functional connectivity prediction pipeline}}
 %
-    {\bfseries\sffamily 2} -- Timeseries signal extraction: For each atlas or
-    ROIs, from Step 1 are used in extracting subject specific timeseries signals.
+%   {\bfseries\sffamily 1} -- Defining Brain ROIs: involves using three
+%   pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
+%   - Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
+%   methods - Linear decomposition models: Group Independent Component
+%   Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
+%   Clustering models: KMeans - Agglomerative with Ward criterion. For each
+%   data-driven method, we build the atlas on training data ($75\%$) on each
+%   split (n=100) and use this atlas for the consecutive step. 
+%   %
+%   {\bfseries\sffamily 2} -- Timeseries signal extraction: For each atlas or
+%   ROIs, from Step 1 are used in extracting subject specific timeseries signals.
+%   %
+%   {\bfseries\sffamily 3} -- Parameterizing functional connectivity between
+%   ROIs,  using  correlation,  partial  correlation  or  tangent  space
+%   embedding
+%   %
+%   {\bfseries\sffamily 4} -- Supervised learning: Classifiers, a classification
+%   model is built to predict groups with two linear classifiers, SVC ($\ell_{1}$ or
+%   $\ell_{2}$ penalization) and ridge regression ($\ell_{2}$ penalization).
+%   %
+%   Cross-validation for 100 splits with $75\%$ training set and remaining
+%   $25\%$ test is used in Step 4, classification setting and reported scores
+%   are Receiver Operating Characteristic and Area Under the Curve (ROC-AUC)
+%   \label{fig:pipeline}
+%end{figure*}
 %
-    {\bfseries\sffamily 3} -- Parameterizing functional connectivity between
-    ROIs,  using  correlation,  partial  correlation  or  tangent  space
-    embedding
-    %
-    {\bfseries\sffamily 4} -- Supervised learning: Classifiers, a classification
-    model is built to predict groups with two linear classifiers, SVC ($\ell_{1}$ or
-    $\ell_{2}$ penalization) and ridge regression ($\ell_{2}$ penalization).
-    %
-    Cross-validation for 100 splits with $75\%$ training set and remaining
-    $25\%$ test is used in Step 4, classification setting and reported scores
-    are Receiver Operating Characteristic and Area Under the Curve (ROC-AUC)
-    \label{fig:pipeline}
-\end{figure*}
-
 %\paragraph{Spread out predictions in a public challenge}
@@
 
-%    \begin{tabular}{llccl}
-%    \toprule
-%    Dataset        &       atlas &          classifier &    measure &
-%    Score \\
-%	%strategy  &        size &    error bar &    error bar \\
-%    \toprule
-%    \multirow{8}{9ex}{ADNI} & AAL &  SVC{$\ell_{1}$} &  correlation & $0.64$ \\
-%                            &           BASC &  Ridge &   Tangent &    $0.71$ \\
-%                            & DictLearn &  SVC{$\ell_{2}$} &   Tangent & $0.75$ \\
-%                        &          Harvard Oxford &  Ridge & Tangent &   $0.66$ \\
-%                            & Group ICA & Ridge & Tangent & $0.75$ \\
-%                  & KMeans & Ridge & Tangent & $0.75$ \\
-%                 & Ward & Ridge & Tangent & $0.71$ \\
-%    \midrule                                            
-%    \multirow{8}{9ex}{} & 30 &   &  \\
-%                  &         100 &   &    \\
-%                  &         300 &   &    \\
-%	          &        1000 &   &    \\
-%    \bottomrule
-%    \end{tabular}}
-%
-%    \centering
-%    \caption{\textbf{Comparison of the atlas impact on prediction accuracy.}
-%        Reported values are the mean of AUC over 100 iterations.
-%        Best predictions are in bold.}
-%     \label{tab:accuracy}
-%     \begin{tabular}{ccccc}
-%         & COBRE & ADNI & ACPI & ADNIDOD \\
-%         \hline\\[-2mm]
-%         AAL       & $.81$ & $.64$ & $.55$ & $\bf .71$ \\
-%         BASC      & $.82$ & $0.71$ & $0.56$ & $0.67$ \\
-%         DictLearn & $\bf{ 0.85}$ & $\bf 0.75$  & $\bf 0.57$ & $\bf 0.68$ \\
-%         HO        & $0.72$ & $0.66$ & $0.57$ & $0.65$ \\
-%         ICA       & $0.83$ & $\bf 0.75$ & $0.55$ & $0.67$ \\
-%         K-Means   & $0.84$ & $\bf 0.75$ & $\bf 0.58$ & $0.68$ \\
-%         Ward      & $0.84$ & $0.71$ & $0.55$ & $\bf 0.69$ \\
-%     \end{tabular}
-% \end{table}
+\begin{table}[tb]
+\small
+\begin{tabularx}{\linewidth}{p{1.2cm}|l|c|c|c|c}
+    \rowcolor{gray!50}
+    Accuracy & COBRE & ADNI & ADNIDOD & ACPI & ABIDE \\ 
+    \hline
+    \rowcolor{gray!13}
+    {\centering $5^{th}$ \\ Percentile} & $74.3\%$ & $62.3\%$ &
+    $53.8\%$ & $41.4\%$ & $64.9\%$\\[.1ex]
+    Median& $87.1\%$ & $76.2\%$ & $67.1\%$ & $56.4\%$ & $70.2\%$\\
+    \rowcolor{gray!13}%
+    {\centering $95^{th}$ \\ Percentile} & $94\%$ & $89.1\%$ &
+    $77.2\%$ & $68.7\%$ & $73.8\%$\\
+    \hline
+\end{tabularx}
+    \caption{\textbf{
+            5th percentile, Median and 95th percentile of accuracy scores in AUC
+            over cross-validation folds ($n=100$) across multi rs-fMRI datasets.}
+            Accuracy scores reported are specific to optimal choices in
+            functional connectivity prediction pipeline: brain atlas,
+            connectivity parameterization, linear classifier as outlined
+            in -- \autoref{tab:pipeline}.
+            Best prediction is achieved with schizophrenia vs control
+            discrimination task on COBRE dataset at $87.1\%$ (median) and
+            $5^{th}$ percentile of scores are around $74.3\%$ and $95^{th}$
+            percentile of scores around $94\%$. Discrimination task on marijuana
+            users vs Non-marijuana users are at the chance level of $56.4\%$
+            (median) on ACPI
+            datasets. We achieved good accuracy with ADNI datasets of $76.2\%$
+            (median) discriminating AD vs MCI and autism vs control
+            discrimination was acheived of accuracy $70.2\%$ (median).
+            vs - versus, AD - Alzheimer's disease, MCI - Mild Cognitive
+            Impairment.}
+    \label{tab:scores}
+\end{table}
+
+%\begin{table}[tb]
+%\small
+%\begin{tabularx}{\linewidth}{p{2.0cm}|c|c|c}
+%    \rowcolor{gray!50}
+%    Dataset & $5^{th}$ Percentile & Median & $95^{th}$ Percentile \\
+%    \hline
+%    \rowcolor{gray!13}
+%    COBRE & $74.3\%$ & $87.1\%$ &  $94\%$ \\
+%    ADNI & $62.3\%$  & $76.2\%$ &  $89.1\%$ \\
+%    \rowcolor{gray!13}
+%    ADNIDOD & $53.8\%$ & $67.1\%$ & $77.2\%$ \\
+%    ACPI &  $41.4\%$ & $56.4\%$  & $68.7\%$ \\
+%    \rowcolor{gray!13}
+%    ABIDE & $64.9\%$ & $70.2\%$ & $73.8\%$  \\
+%    \hline
+%\end{tabularx}
+%\end{table}
+
+General formulation: What we are trying to show in this section. The pipeline
+prediction capability across diverse phenotypes and the recommendations of
+methods at each step which showed significant/consistent impact on diverse
+tasks. (Can be removed later).
+
+In this section, we outline the results obtained by systematic comparisons
+made on methodological choices employed at each step in the functional
+connectivity prediction pipeline over diverse phenotypes from multi
+rs-fMRI datasets.
+Particularly, we show which choices have made an significant impact in the
+prediction pipeline by measuring the relative change in the prediction
+scores (AUC), over all the choices at each step such as Brain ROIs,
+Connectivity Parameterization and Classification
+using Machine Learning. We start with results of relative change over:
+choices of classifiers, choices of connectivity parameterization and
+choices of brain atlases.
+
+We also report the best pipeline prediction accuracy scores in AUC across
+multi rs-fMRI datasets.
+
+\begin{table}[tb]
+\small
+\begin{tabularx}{\linewidth}{l|p{1.55cm}|c|c|c}
+    \rowcolor{gray!50}
+    Brain atlas  & Connectome & Classifier & Regions &
+    Dimensions \\
+    \hline
+    DictLearn & Tangent embedding &  SVC-$\ell{_2}$ &  Yes & 60 \\
+\end{tabularx}
+    \caption{\textbf{
+        Prediction choices at each step in resting state functional connectivity
+        pipeline: Brain atlas, Connectome, Classifier}.
+        The results are outlined after relatively comparing at each step, over the
+        choices of classifiers, connectivity parameterization methods and brain
+        atlases (pre-defined or data driven atlases) as shown in --
+        \autoref{fig:impact_classifier}, \autoref{fig:impact_connectivity} and
+        \autoref{fig:impact_atlas}. Functional brain atlases
+        learned using Online Dictionary Learning (DictLearn) with
+        number of resting state networks=$60$ and spliting networks to regions are
+        shown as good choices in the prediction pipeline with Tangent based
+        connectivity matrix parameterization and Support Vector Linear
+        Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).}
+    \label{tab:pipeline}
+\end{table}
+
  \subsection{Choice of classifier}
+ \paragraph{Which classifier is good enough for a binary classification
+     problems but across diverse tasks ? Is it really important to address
+     this question ? How do you pick your choice of classifier which
+     is good enough to perform prediction given heterogeneity in the tasks ?}
+
+     The comparisons between three different choices of linear classifiers
+     (SVC-$\ell{_1}$, SVC-$\ell{_2}$, Ridge) are outlined in
+     \autoref{fig:impact_classifier}, shows the relative impact made in the
+     classification of diverse tasks (COBRE, ADNI, ADNIDOD, ACPI, ABIDE) measured
+     over all classifiers while demeaning the impact from other steps in the
+     pipeline (Brain ROIs, Connectivity Parameterization).
+
+     We chose to compare two most commonly used linear classifiers
+     (SVC, Ridge) in rs-fMRI prediction problems.
+     The choices of linear classifiers have shown significant variations in
+     relation to the prediction of diverse tasks.
+     From \autoref{fig:impact_classifier}, we summarize that $\ell{_2}$
+     regularized classifiers SVC and Ridge outperformed $\ell{_1}$ regularized
+     SVC classifier across tasks from multi rs-fMRI datasets. Both,
+     SVC-$\ell{_2}$ and Ridge showed almost equal impact in prediction across all
+     datasets. In almost all the predicition tasks, sparse classifier perform
+     less in finding good functional features discrimination at rest.
+     The most preferable choices in prediction of phenotypes at rest fMRI are
+     dense classifiers predicting significantly target features lying in dense
+     representations. The choice of classifier in diagnostic evaluation is
+     important.
 
@@
     \centerline{%
-    \includegraphics[width=.8\linewidth]{impact_plot_classifier.pdf}%
+    \includegraphics[width=0.8\linewidth]{figures/impact_plot_classifier.pdf}%
     }%
-    \caption[choice of classifier]{\textbf{Impact of classifier choices on
-    prediction scores}
-\label{fig:impact_classifier}}
+    \caption[choice of classifier]{\textbf{The impact of classifier
+            choices in functional connectivity prediction pipeline over
+            diverse tasks}:
+            The figure shows the relative change to mean in prediction scores
+            (AUC) over all the classifiers SVC-$\ell{_1}$, SVC-$\ell{_2}$,
+            Ridge. Each boxplot depicts the prediction
+            impact of each classifier grouped together for all datasets
+            (COBRE, ADNI, ADNIDOD, ACPI, ABIDE) whereas each data point on top
+            of each boxplot is a split of impact over each dataset.
+            From the baseline=$0.0$, $\ell{_2}$ regularized choices such as
+            SVC-$\ell{_2}$ and Ridge has
+            shown relatively positive impact in prediction, significant
+            across datasets. SVC-$\ell_{1}$ choice has shown negative impact in
+            prediction across all datasets. For each choice, the prediction pipeline
+            was ran in cross-validation framework with $n=100$ random splits
+            and shuffled with $75\%$ training set and $25\%$ test set.
+            } 
+\label{fig:impact_classifier}
 \end{figure}
@@
 \subsection{Choice of connectivity parameterization}
+In \autoref{fig:impact_connectivity}, we show the relative impact of
+the measure of covariance matrix/connectome method made on the classification
+of diverse tasks from multi rs-fMRI datasets. We took the relatively mean over
+all the connectivity parameterization methods (Full correlation, Partial
+correlation, Tangent space parameterization) while demeaned the effect of
+variance from remaining steps in the pipeline such as Brain ROIs and Linear
+Classifiers.
+
+From \autoref{fig:impact_connectivity}, we summarize that connectomes built
+with tangent space parameterization outperformed other standard methods
+such as full correlations and partial correlations.
+Tangent space parameterization method has shown significantly positive impact
+and consistent in finding the covariances across pair of brain ROIs, able
+to use in discrimination across diverse tasks. From
+\autoref{fig:impact_connectivity}, it is also interesting to see comparisons
+between full correlation and partial correlation methods. Full correlation
+has made an positive prediction impact on ADNI dataset to discriminate
+between Alzheimer's disease (AD) and Mild Cognitive Impairment (MCI). Partial
+correlation performed well in discriminating Marijuana users and Non-marijuana
+users. Between full correlation and partial correlation, only predicting few
+tasks has high impact where tangent space parameterization has significant
+impact across diverse targets.
+
+These results suggest that probabilistic approach leads to finding good
+selection of connectivity features across brain regions to compare them across
+subjects.
 
@@
     \centerline{%
-    \includegraphics[width=\linewidth]{impact_plot_measure.pdf}%
+    \includegraphics[width=0.8\linewidth]{figures/impact_plot_measure.pdf}%
     }%
-    \caption[choice of classifier]{\textbf{Impact of connectivity
-            parameterization method choices on prediction scores}
+    \caption[choice of connectome]{\textbf{The impact of connectivity
+            parameterization methods in functional connectivity prediction
+            pipeline over diverse tasks}:
+            Boxplot (gray) ($x-axis$) is a relatively change in prediction scores
+            (AUC) over all the connectivity methods - Full correlation, Partial
+            correlation and Tangent space parameterization. Each boxplot
+            depicts the prediction impact of each connectivity method grouped
+            together for all datasets. Each data
+            point on top of each boxplot shows the impact separately
+            over each dataset (COBRE, ADNI, ADNIDOD, ACPI, ABIDE). Full and Partial
+            correlation based connectivity performed less, showed
+            large variations and minimal impact on predicting diverse tasks.
+            While prediction using tangent space based connectivity
+            parameterization has showed good impact and consistent where
+            data points are falling almost in the positive range from
+            baseline=$0.0$. For each choice, the prediction pipeline
+            was ran in cross-validation framework with $n=100$ random splits
+            and shuffled with $75\%$ training set and $25\%$ test set.
 \label{fig:impact_connectivity}}
@@
 
-\subsection{Choice of atlas methods: Either regions or networks}
+\subsection{Choice of brain atlases}
+To understand better the choice of brain atlas in prediction pipeline,
+we first systematically compared the atlases composed of brain regions and
+networks across enormous learning dimensions and
+made an empirical choice of dimension on each atlas as outlined in
+\autoref{fig:effect_size_in_regions} and \autoref{fig:effect_size_in_networks}.
+Second, we adapted this comparison to study the relative impact of each
+brain atlas made in pipeline prediction over diverse tasks as
+outlined in \autoref{fig:impact_atlas}. Brain atlases have made a huge
+impact in the prediction pipeline and each atlas has showed its significant
+impact in predicting diverse tasks across all multi rs-fMRI datasets.
+Data-driven atlases such as Ward, K-Kmeans, GroupICA and Online Dictionary
+Learning had made a significant impact in predicting on COBRE and ADNI
+datasets. While pre-defined anatomical atlases such as AAL and Harvard Oxford
+have made less impact in predicting diverse tasks. Harvard Oxford is only
+performing good on ACPI datasets. Out of all atlases, Online dictionary
+learning had showed good positive impact where the relative scores across
+diverse tasks are of positive values except in ADNIDOD.
+
+\subsubsection{Choice of dimensionality with Brain regions}
+In \autoref{fig:effect_size_in_regions}, we show the impact of the
+learning dimensionality in brain atlases composed of regions
+made on prediction scores. The
+data-driven atlas extraction methods such as GroupICA (ICA), Online Dictionary
+Learning (DictLearn), KMeans with enormous dimensions varied in ${40, 60,
+80, 100, 120, 150, 200, 300}$, and a pre-defined functional atlas BASC built with
+dimensionality varied in ${36, 64, 122, 197, 325, 444}$ are used for
+comparisons to make an optimal choice of dimension for each method. From
+\autoref{fig:effect_size_in_regions}, we chose optimal choice of
+learning dimensionality with GroupICA as $80$, Online Dictionary Learning as
+$60$, KMeans as $100$, BASC as $122$. We made the choice of learning
+dimensionality which made high positive impact from the baseline=$0.0$ for
+all multi rs-fMRI datasets - COBRE, ADNI, ADNIDOD, ACPI, ABIDE. We did not
+study the already imposed spatially constrained Ward method in brain atlases
+comparisons composed of regions.
+
+The choices of dimensionality learned for each atlas are further
+used in comparing
+for optimal choice between brain regions and brain networks as outlined in
+\autoref{fig:regions_vs_nonregions} to study the comparisons of choices of
+brain atlases.
 
@@
     \centerline{%
-    \includegraphics[width=\linewidth]{impact_plot_atlas.pdf}%
+    \includegraphics[width=\linewidth]{figures/impact_plot_atlas.pdf}%
     }%
-    \caption[choice of atlas]{\textbf{Impact of atlas choices
-        on prediction scores}
+    \caption[choice of atlas]{\textbf{The impact of brain atlases in
+            functional connectivity prediction pipeline over diverse tasks}:
+            Boxplot (gray) depicts the relatively change in prediction
+            scores response in AUC ($x-axis$) over all the atlas choices on
+            ($y-axis$) - AAL, Harvard Oxford, BASC, Ward, K-Means, Group ICA,
+            Online Dictionary Learning grouped for all the multi rs-fMRI
+            datasets. While each data point on top of each boxplot outlines
+            the prediction impact separately for each dataset - COBRE (black),
+            ADNI (green), ADNIDOD (dark red), ACPI (pink), ABIDE (brown).
+            Learning atlases on the brain data had showed positive prediction
+            impact significant over predicting diverse tasks, in particular,
+            Online Dictionary Learning. The impact of using pre-defined
+            anatomical atlases - AAL and Harvard Oxford is significantly less
+            and has huge variance in the prediction of diverse tasks (highly
+            dependant on the phenotype). The comparisons in this figure
+            are made on particular choice of dimension chosen for each
+            data-driven learning atlas: such as Ward of $120$ brain
+            parcellations, K-Means of $100$ brain parcellations, Group ICA of
+            $80$ brain networks and splitted into regions, Online Dictionary
+            Learning of $60$ brain networks splitted into regions. We also
+            pick dimension of one functional pre-defined atlas: BASC of $122$
+            brain networks split into regions. These choices are made after
+            systematic exploration across all dimensions used
+            in the experiments to build the brain atlases for prediction. As
+            showed in \autoref{fig:effect_size_in_regions} and
+            \autoref{fig:effect_size_in_networks}, where choices on dimensions
+            are made between regions or networks/parcellations. In
+            \autoref{fig:regions_vs_nonregions}, where choice is made between
+            regions or without regions. For all comparisons, the prediction
+            pipeline was ran in cross-validation framework with $n=100$
+            random splits and shuffled with $75\%$ training set and $25\%$
+            test set.
     \label{fig:impact_atlas}}
@@
 
-\paragraph{Effect of dimensionality: Brain regions}
-
 \begin{figure}
     \centerline{%
-	\includegraphics[width=\linewidth]{dot_plot_n_regions_suppressed_background.pdf}%
+	\includegraphics[width=1.1\linewidth]{figures/dot_plot_n_regions_suppressed_background.pdf}%
     }%
-    \caption[]{\textbf{Effect of dimensionality: Choice of brain regions} {For
-            each of four atlases (ICA, DictLearn, KMeans, BASC) driven with region
-            extraction, we show the measure of effect on prediction scores obtained by
-            removing the mean effect of group relatively over all
-            cross-validation splits and datasets.
-
-            What we obtain then, is the demeaned score for each split and for each
-            dataset.
-
-            Given that, we plot here: for each atlas, we took the average of
-            calculated demeaned scores over all splits which is showed on y-axis
-            as choice of vary in dimensionality as showed on x-axis.
-
-            For each atlas, we then see the effect of each dataset (each unique color)
-            by projecting an error bar plot with $95\%$ confidence interval on each
-            averaged score shown as violin plot in gray color.
-
-            Given the plots, we choose here the best dimensionality in ICA of
-            $80$, and DictLearn of $60$, KMeans of $120$ and BASC of $122$.
-
-            These references in finding an optimalilty dimensionalities are
-            then used for further comparisons of choosing the best atlas
-            method.}
+    \caption[]{\textbf{Impact of dimensionality in learning the prediction with atlas of
+            brain regions}: For each atlas - ICA, DictLearn, KMeans, BASC),
+            violinplot (gray) depicts the relatively mean change in prediction
+            scores response in AUC ($y-axis$) over all the dimensionalities
+            ($x-axis$). On top of each violinplot are the error bars with
+            $95\%$ confidence interval across all datasets - COBRE (black),
+            ADNI (green), ADNIDOD (dark red), ACPI (pink), ABIDE (brown).
+            The optimal dimensionality (vertical red arrow) with
+            ICA is $80$, DictLearn is $60$,
+            KMeans is $100$ and BASC is $122$ which has showed significantly
+            positive impact (above baseline=$0.0$) across all datasets. We
+            reduce the effect of variance by keeping the prediction scores
+            from the pipeline only to tangent space parameterization and
+            SVC-$\ell{_2}$ classifier. The pipeline prediction was ran in
+            cross-validation framework with $n=100$ random splits shuffled with
+            $75\%$ training set and $25\%$ test set.}
     %
     \label{fig:effect_size_in_regions}
-    }
 \end{figure}
 
-To understand better the choice of atlas defined with or without region
-extraction as a function of vary in dimensionality, we chose to see the mean
-effect on prediction scores overall the cross validation folds with respect to
-four reference atlases (ICA, Dictionary Learning, KMeans and BASC) with
-various dimensionalities. \autoref{fig:effect_size_in_regions} outlines to choose
-between the optimal dimensionality for each atlas as a function of regions.
-
-\paragraph{Effect of dimensionality: Brain networks/parcellations}
+\subsubsection{Choice of dimensionality with Brain networks or parcellations}
 %
+In \autoref{fig:effect_size_in_networks}, the
+atlas extraction methods such as GroupICA (ICA), Online Dictionary
+Learning (DictLearn), KMeans and Ward with enormous dimensions varied in ${40, 60,
+80, 100, 120, 150, 200, 300}$, and a pre-defined functional atlas BASC built with
+dimensionality varied in ${36, 64, 122, 197, 325, 444}$ are used for
+comparisons to make an optimal choice of dimension for each method (without
+regions). From
+\autoref{fig:effect_size_in_networks}, we chose optimal choice of
+learning dimensionality with GroupICA as $80$, Online Dictionary Learning as
+$60$, KMeans as $100$, Ward as $120$ and BASC as $122$. We made an empirical
+choice of learning dimensionality by choosing the atlases which made high
+positive impact
+for all multi rs-fMRI datasets - COBRE, ADNI, ADNIDOD, ACPI, ABIDE. If any of the
+both choice in each atlas have made an equal impact, we took the least
+probable dimensionality as an optimal choice.
+The choices of dimensionality learned for each atlas are further
+used in comparing
+for optimal choice between brain regions and brain networks as outlined in
+\autoref{fig:regions_vs_nonregions} to study the comparisons of choices of
+brain atlases.
 \begin{figure}
     \centerline{%
-	\includegraphics[width=\linewidth]{dot_plot_parcellations_suppressed_background2.pdf}%
+	\includegraphics[width=1.1\linewidth]{figures/dot_plot_parcellations_suppressed_background.pdf}%
     }%
-    \caption[]{\textbf{Effect of dimensionality: Choice of brain
-        networks/parcellations} {Atlases based on networks: ICA, DictLearn,
-            BASC whereas based on parcellations are KMeans and Ward. In total,
-            we are comparing here five brain atlases each driven without
-            region extraction.
-
-            We show the measure of effect on prediction scores obtained by
-            removing the mean effect of group relatively over all cross-validation
-            splits and datasets.
-
-            As demonstrated in \autoref{fig:effect_size_in_regions}, we show
-            the same the demeaned score for each split and for each dataset
-            but this time without region extraction.
-
-            Given that, we plot here: for each atlas, we took the average of
-            calculated demeaned scores over all splits which is showed on y-axis
-            as choice of vary in dimensionality as showed on x-axis.
-
-            For each atlas, we then see the effect of each dataset (each unique color)
-            by projecting an error bar plot with $95\%$ confidence interval on each
-            averaged score shown as violin plot in gray color.
-
-            Given the plots, we choose here the best dimensionality in
-            networks: ICA of $80$, and DictLearn of $60$, KMeans of $120$ and BASC
-            of $122$ and Ward of $120$.
-
-            These references in finding an optimalilty dimensionalities without
-            region extraction are then used for further comparisons of choosing
-            the best atlas method.}
+    \caption[]{\textbf{Impact of dimensionality in learning the prediction
+            with atlas of brain networks/parcellations}
+            For each atlas composed of networks (ICA, DictLearn, BASC)
+             and parcellations (KMeans and Ward), violinplot (gray)
+             depicts the relatively mean change in prediction
+            scores response in AUC ($y-axis$) over all the dimensionalities
+            ($x-axis$). On top of each violinplot are the error bars with
+            $95\%$ confidence interval across all datasets - COBRE (black),
+            ADNI (green), ADNIDOD (dark red), ACPI (pink), ABIDE (brown).
+            The optimal dimensionality (vertical red arrow) with
+            ICA is $80$, DictLearn is $60$,
+            KMeans is $100$ , Ward is $120$ and BASC is $122$ which has
+            showed significantly
+            positive impact (above baseline=$0.0$) across all datasets. We
+            reduce the effect of variance by keeping the prediction scores
+            from the pipeline only to tangent space parameterization and
+            SVC-$\ell{_2}$ classifier. The pipeline prediction was ran in
+            cross-validation framework with $n=100$ random splits shuffled with
+            $75\%$ training set and $25\%$ test set.}
     %
     \label{fig:effect_size_in_networks}
-    }
 \end{figure}
 
-\paragraph{Which is better: Brain atlases with regions or without regions}
-Given the outlining the choice of optimal dimensionality of brain atlases with
-or without regions extracted as shown in \autoref{fig:effect_size_in_regions}
-and \autoref{fig:effect_size_in_networks}, we compare them to see which is
-better in prediction. Prediction using atlases build with regions or
-using atlases build with networks. As shown in
-\autoref{fig:regions_vs_nonregions}, and atlas GroupICA or ICA, predicting
+\subsubsection{Which is better: Brain atlases with regions or without regions}
+Given the outlined choices of optimal dimensionality in brain atlases composed
+of regions and networks as shown in \autoref{fig:effect_size_in_regions}
+and \autoref{fig:effect_size_in_networks}, we compare now to study which has
+better impact in prediction. Prediction using atlases composed of regions or
+networks. As shown in
+\autoref{fig:regions_vs_nonregions}, atlases with GroupICA or ICA, predicting
 using regions is better rather than using only networks. Whereas for
@@
 
+%\begin{table}[tb]
+%\footnotesize%
+%\small
+%\rowcolors{2}{gray!15}{white}%
+%\begin{tabularx}{\linewidth}{p{1.0cm}|l|l|l|l}
+%    \textbf{Brain atlas} & \textbf{Connectivity}
+%    & \textbf{Classifier} & \textbf{Regions} & \textbf{Dimensions} \\
+%    %\hline
+%    DictLearn & Tangent Embedding & SVC-$\ell{_2}$ & Yes & 60 \\
+%    %\bottomrule
+%\end{tabularx}
+%\end{table}
+
 \begin{figure}
     \centerline{%
-	\includegraphics[width=\linewidth]{violin_plot_mean_score_region_extraction_ica_dict_kmeans.pdf}%
+	\includegraphics[width=1.\linewidth]{figures/violin_plot_mean_score_region_extraction_ica_dict_kmeans.pdf}%
     }%
-    \caption[regions vs non regions]{\textbf{Which is better for prediction: regions or
-        without regions}
+    \caption[regions vs non regions]{\textbf{Which is better for prediction:
+            Brain regions or Brain networks}
         For each atlas (ICA, DictLearn, KMeans and BASC), we show here the
@@
 
-\section{Supplementary material}
-
-\begin{figure}
-    \centerline{%
-	\includegraphics[width=.8\linewidth]{n_regions_vs_dimensionality.pdf}%
-    }%
-    \caption{\textbf{Number of regions extracted with dimensionality}
-    %
-    %
-    \label{fig:n_regions_dim}
-    }
-\end{figure}
-
-\begin{table}[t]
-    \begin{tabular}{llllrlll}
-        \toprule
-        & Atlas &    Classifier & Measure &  Dimensionality & Regions & 
-        ROC\textunderscore AUC &  Dataset \\
-        \midrule
-        &  Online Dictionary Learning & SVC-$\ell{_2}$ & Tangent & 60 & yes &
-        0.86\$\textbackslashpm\$0.06 &    COBRE \\
-        & K-Means & Ridge & Tangent & 120 & no &
-        0.76\$\textbackslashpm\$0.09 &
-        ADNI \\
-        &                            AAL &  SVM-\$\textbackslashell\_1\$ &
-        Tangent &             116 &      no &  0.72\$\textbackslashpm\$0.08 &
-        ADNIDOD \\
-        &                        K-Means &  SVM-\$\textbackslashell\_2\$ &
-        Partial \textbackslashn Correlation &             120 &      no &
-        0.58\$\textbackslashpm\$0.08 &     ACPI \\
-        &                            ICA &  SVM-\$\textbackslashell\_2\$ &
-        Tangent &              80 &     yes &   0.7\$\textbackslashpm\$0.03 &
-        ABIDE \\
-        \bottomrule
-    \end{tabular}
-\end{table}
 %\begin{figure}
-%    \includegraphics[width=\linewidth]{figures/performance_vs_size_2.pdf}%
-%    \caption{\textbf{Reported accuracy and sample size}
-    %
-%    The various plots show reported prediction accuracy as a
-%    function of sample size for the studies in different the
-%    reviews considered in \autoref{fig:sample_size}.
-    %
-%    The black line and grey area represent the $p=0.05$ threshold with a
-%    binomial null model, which, as shown in the results section, is
-%    likely to be optimistic.
-    %
-%    The lines are Lowess fit to the data: robust non-parametric local
-%    regression.
-    %
-%    \label{fig:reported_accuracy}
+%    \centerline{%
+%	\includegraphics[width=.8\linewidth]{n_regions_vs_dimensionality.pdf}%
+%    }%
+%    \caption{\textbf{Number of regions extracted with dimensionality}
+%    %
+%    %
+%    \label{fig:n_regions_dim}
 %    }
 %\end{figure}
+\paragraph{Choice of brain atlas}
+
+\section{Discussion:}
+
+In this section, we talk about the right trends and recommendations which
+should be made at each step in the functional connectivity prediction
+pipeline.
 
 \section{Conclusion:}
-
-% Acquiring large quality datasets is intrinsically a challenge in
-% neuroimaging, whether it is psychiatric or cognitive
-% (repetition effects)
-
-%%% Position with regards to papers
-
-% Recall the power-failure paper. Stress that the problem that I report
-% is not a failure of the predictive models, which is also a risk. 
-% The intuitions that we gain from standard statistics do not carry over
-% well: One difference with standard statistics (as in the power-failure paper)
-% is that the effect size matter. On the opposite, in classification,
-% only correct vs incorrect is counted, which is the power and the
-% limitation of the methods
-
-% The paper by poldrack 
-%\cite{poldrack2016scanning}
-
-% cite Braga-Neto, "Is cross-validation valid for small-sample
-% microarray classification?" to underline that this has been seen in
-% genomics
-
-% Stress that the problem is not fixed by better classifiers (my sport)
-
-% Say that I have myself been overly optimistic and confident in my
-% results in the development of decoders, some of which have not
-% reproduced \cite{michelsupervised} though the core mathematical
-% intuitions were correct \cite{rena}
 
@@
 
-\small
+\section{Supplementary material}
 %\bibliographystyle{elsarticle-num-names}
@@
 
-%\appendix
-%\renewcommand{\thefigure}{A\arabic{figure}}
-%\setcounter{figure}{0}
-%\renewcommand{\thetable}{A\arabic{table}}
-%\setcounter{table}{0}
-
-%\begin{figure}%
-    %\center%
-    %\includegraphics[width=.7\linewidth]{github_code/sem_vs_error.pdf}%
-    %\medskip
-
-%    {\small\sffamily%
-%    \begin{tabular}{llrrr}
-    %\toprule
-%	CV        &       train &          SEM &    empirical \\
-%	strategy  &        size &    error bar &    error bar \\
-%    \toprule
-%    \multirow{4}{9ex}{LOO} & 30 &  $\pm 13.8\%$ &  $\pm 18.9\%$ \\
-%		&           100 &  $\pm 7.4\%$ &   $\pm 10.3\%$ \\
-%	        &           300 &  $\pm 4.1\%$ &   $\pm  5.9\%$ \\
-%		&          1000 &  $\pm 2.2\%$ &   $\pm  2.9\%$ \\
-%    \midrule                                            
-%    \multirow{4}{9ex}{50 splits,\\20\% test} & 30 &  $\pm 3.4\%$ & $\pm 15.3\%$ \\
-%                  &         100 &  $\pm 2.0\%$ &   $\pm  8.1\%$ \\
-%                  &         300 &  $\pm 1.1\%$ &   $\pm  4.1\%$ \\
-%	          &        1000 &  $\pm 0.6\%$ &   $\pm  2.1\%$ \\
-    %\bottomrule
-%    \end{tabular}}
-%    \caption{\textbf{}
-%    \label{fig:error_vs_sem}}
-%\end{figure}
-
-%\begin{figure}[t]
-%    \centerline{%
-%     \includegraphics[width=.8\linewidth]{github_code/dimensionality_results.pdf}%
-%     \llap{\raisebox{.72\linewidth}{%
-%	\parbox{.86\linewidth}{\bfseries\sffamily Binomial\\law}}}%
-%    }%
-%
-%    \caption{\textbf{Distribution of errors as given by a binomial law}
-%    Different between the observation prediction error and the 
-%    population value of the probability of error for different sample sizes.
-%    The bar and whiskers indicate the median
-%    and the 5\raisebox{.5ex}{\tiny th} and 95\raisebox{.5ex}{\tiny th}
-%    percentile. 
-%    \label{fig:binomial}}
-%\end{figure}
-
 \end{document}

### 2017-05-27 rs_study/experiments/paper/figures/plot_roc_auc_scores.py

@@ -70,7 +70,7 @@ data_all = data_all.drop('Unnamed: 0', axis=1)
 
 # Choosing the optimal choice in dimensionality for each atlas
 dic_model_dim = OrderedDict([('ica', 80),
-                            ('kmeans', 120),
+                            ('kmeans', 100),
                             ('dictlearn', 60),
                             ('ward', 120),
                             ('aal_spm12', 116),

### 2017-06-02 rs_study/experiments/paper/paper.tex
iter

@@
 \small
-\begin{tabularx}{\linewidth}{p{1.2cm}|l|c|c|c|c}
+\begin{tabularx}{\linewidth}{p{1.2cm}|p{1.0cm}|p{0.7cm}|p{1.42cm}|l|l}
     \rowcolor{gray!50}
-    Accuracy & COBRE & ADNI & ADNIDOD & ACPI & ABIDE \\ 
+    \centering{Accuracy} & COBRE & ADNI & ADNIDOD & ACPI & ABIDE \\
     \hline
     \rowcolor{gray!13}
+    Median& $87.1\%$ & $76.2\%$ & $67.1\%$ & $56.4\%$ & $70.2\%$\\
+    % \rowcolor{gray!13}%
     {\centering $5^{th}$ \\ Percentile} & $74.3\%$ & $62.3\%$ &
     $53.8\%$ & $41.4\%$ & $64.9\%$\\[.1ex]
-    Median& $87.1\%$ & $76.2\%$ & $67.1\%$ & $56.4\%$ & $70.2\%$\\
-    \rowcolor{gray!13}%
+    \rowcolor{gray!13}
     {\centering $95^{th}$ \\ Percentile} & $94\%$ & $89.1\%$ &
@@
     \caption{\textbf{
-            5th percentile, Median and 95th percentile of accuracy scores in AUC
+            Median, 5th percentile and 95th percentile of accuracy scores in AUC
             over cross-validation folds ($n=100$) across multi rs-fMRI datasets.}
@@
             functional connectivity prediction pipeline: brain atlas,
-            connectivity parameterization, linear classifier as outlined
-            in -- \autoref{tab:pipeline}.
+            connectivity parameterization, linear classifier as studied
+            from -- \autoref{fig:impact_classifier},
+            \autoref{fig:impact_connectivity}, \autoref{fig:impact_atlas}.
+            Functional brain atlases
+            learned using Online Dictionary Learning (DictLearn) with
+            number of resting state networks=$60$ and spliting networks to regions are
+            shown as good choices in the prediction pipeline with Tangent based
+            connectivity matrix parameterization and Support Vector Linear
+            Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).
             Best prediction is achieved with schizophrenia vs control
@@
 
-\begin{table}[tb]
-\small
-\begin{tabularx}{\linewidth}{l|p{1.55cm}|c|c|c}
-    \rowcolor{gray!50}
-    Brain atlas  & Connectome & Classifier & Regions &
-    Dimensions \\
-    \hline
-    DictLearn & Tangent embedding &  SVC-$\ell{_2}$ &  Yes & 60 \\
-\end{tabularx}
-    \caption{\textbf{
-        Prediction choices at each step in resting state functional connectivity
-        pipeline: Brain atlas, Connectome, Classifier}.
-        The results are outlined after relatively comparing at each step, over the
-        choices of classifiers, connectivity parameterization methods and brain
-        atlases (pre-defined or data driven atlases) as shown in --
-        \autoref{fig:impact_classifier}, \autoref{fig:impact_connectivity} and
-        \autoref{fig:impact_atlas}. Functional brain atlases
-        learned using Online Dictionary Learning (DictLearn) with
-        number of resting state networks=$60$ and spliting networks to regions are
-        shown as good choices in the prediction pipeline with Tangent based
-        connectivity matrix parameterization and Support Vector Linear
-        Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).}
-    \label{tab:pipeline}
-\end{table}
+%\begin{table}[tb]
+%\small
+%\begin{tabularx}{\linewidth}{l|p{1.55cm}|c|c|c}
+%    \rowcolor{gray!50}
+%    Brain atlas  & Connectome & Classifier & Regions &
+%    Dimensions \\
+%    \hline
+%    DictLearn & Tangent embedding &  SVC-$\ell{_2}$ &  Yes & 60 \\
+%\end{tabularx}
+%    \caption{\textbf{
+%        Prediction choices at each step in resting state functional connectivity
+%        pipeline: Brain atlas, Connectome, Classifier}.
+%        The results are outlined after relatively comparing at each step, over the
+%        choices of classifiers, connectivity parameterization methods and brain
+%        atlases (pre-defined or data driven atlases) as shown in --
+%        \autoref{fig:impact_classifier}, \autoref{fig:impact_connectivity} and
+%        \autoref{fig:impact_atlas}. Functional brain atlases
+%        learned using Online Dictionary Learning (DictLearn) with
+%        number of resting state networks=$60$ and spliting networks to regions are
+%        shown as good choices in the prediction pipeline with Tangent based
+%        connectivity matrix parameterization and Support Vector Linear
+%        Classifier with $\ell{_2}$ (SVC-$\ell{_2}$).}
+%    \label{tab:pipeline}
+%\end{table}
 
@@
     \centerline{%
-	\includegraphics[width=1.\linewidth]{figures/violin_plot_mean_score_region_extraction_ica_dict_kmeans.pdf}%
+	\includegraphics[width=1.\linewidth]{figures/regions_nonregions_difference_distribution.pdf}%
     }%
@@
 
-%\begin{figure}
-%    \centerline{%
-%	\includegraphics[width=.8\linewidth]{n_regions_vs_dimensionality.pdf}%
-%    }%
-%    \caption{\textbf{Number of regions extracted with dimensionality}
-%    %
-%    %
-%    \label{fig:n_regions_dim}
-%    }
-%\end{figure}
+\begin{figure}
+    \centerline{%
+	\includegraphics[width=0.5\paperwidth]{figures/brainrois.pdf}%
+    }%
+    \caption{\textbf{Brain regions/parcellations using ICA, DictLearn, KMeans,
+        Ward}
+    %
+    %
+    \label{fig:brain_rois}
+    }
+\end{figure}
 \paragraph{Choice of brain atlas}

### 2017-06-02 rs_study/experiments/plotting_scripts_for_paper/regions_vs_nonregions_comparison_in_violinplot.py

@@ -54,7 +54,7 @@ def stripplot_mean_score(df, save_path, atlas=None, suffix=None, x=None,
                    width=0.5, ax=axx)
 
     sns.stripplot(data=df, x=x, y=y, hue=hue, edgecolor='gray',
-                  size=5, split=True, palette=datasets_palette, jitter=jitter,
+                  size=3, split=True, palette=datasets_palette, jitter=jitter,
                   ax=axx)
 
     axx.set_xlabel('')
@@ -66,9 +66,9 @@ def stripplot_mean_score(df, save_path, atlas=None, suffix=None, x=None,
     axx_xticklabels = []
     for x in axx.get_xticks():
         if x > 0:
-            axx_xticklabels.append('+' + str(x) + '$\%$')
+            axx_xticklabels.append('+' + str(x))
         else:
-            axx_xticklabels.append(str(x) + '$\%$')
+            axx_xticklabels.append(str(x))
     axx.set_xticklabels(axx_xticklabels)
     # xticklabels=string.capitalize()
     # yticklabels=string.capitalize(axx.get_yticklabels())
@@ -155,7 +155,7 @@ for i, (key, ax) in enumerate(zip(atlases, axes)):
     demeaned_scores = df.groupby(['classifier', 'measure', 'dataset',
                                   'dimensionality'])['scores'].transform(demean)
 
-    df['demeaned_scores'] = demeaned_scores * 100
+    df['demeaned_scores'] = demeaned_scores
 
     ########################################################################
     # plot to pdf, png and svg

### 2017-06-02 rs_study/experiments/paper/figures/plot_diff_regions_nonregions.py
Figures: plot distribution difference on regions and networks

@@ -1,0 +1,166 @@
+"""Plot to diff between regions and non-regions (networks)
+"""
+
+
+def change_label_name(row, label, new_names):
+    row[label] = new_names[row[label]]
+    return row
+
+###############################################################################
+# csv results
+import os
+
+covariance_estimator = 'LedoitWolf'
+dataset_paths = dict()
+dataset_names = ['COBRE', 'ADNI', 'ADNIDOD', 'ACPI', 'ABIDE']
+atlases = ['ICA', 'DictLearn', 'KMeans', 'BASC']
+
+extensions = {'ICA': 'scores_ica.csv',
+              'DictLearn': 'scores_dictlearn.csv',
+              'KMeans': 'scores_kmeans.csv',
+              'BASC': 'scores_basc.csv'}
+
+base_path = os.path.join('../../prediction_scores', covariance_estimator)
+
+for dataset in dataset_names:
+    paths = []
+    for atlas in atlases:
+        for folder in ['region_extraction', 'networks', 'parcellations']:
+            atlas_path = os.path.join(atlas, folder, extensions[atlas])
+            path = os.path.join(base_path, dataset, atlas_path)
+            if os.path.exists(path):
+                paths.append(path)
+        dataset_paths[dataset] = paths
+
+###############################################################################
+# load and extract the data to best choices
+from collections import OrderedDict
+
+import pandas as pd
+import load_data
+
+data_list = []
+for name in dataset_names:
+    this_data_path = dataset_paths[name]
+    this_data = load_data._pandas_data_frame_list_of_paths_concat(this_data_path)
+    data_list.append(this_data)
+
+whole_data = pd.concat(data_list)
+whole_data = whole_data.drop('Unnamed: 0', axis=1)
+
+dic_model_dim = OrderedDict([('ica', 80),
+                             ('kmeans', 120),
+                             ('dictlearn', 60),
+                             ('basc', 122)
+                             ])
+
+choices_data = pd.DataFrame()
+for key in dic_model_dim.keys():
+    choices_data = choices_data.append(
+        whole_data[(whole_data['atlas'] == key) &
+                   (whole_data['dimensionality'] == dic_model_dim[key])])
+#############################################################################
+# Calculate demeaned scores on choices data
+
[…]

### 2017-06-07 submissions/news_2017/abstract.tex
Submissions: Abstract for NeWS conference 2017

%\documentstyle[12pt]{article}
\documentclass[12pt]{article}

\begin{document}

\begin{center}
{\large\bf Towards a better predictive model from rest fMRI: benchmarks across
multiple phenotypes}\\[4mm]
\end{center}

\begin{center}
Kamalaker Dadi$^a$$^b$, Darya Chyzhyk$^a$$^b$, Alexandre Abraham$^a$$^b$,
Mehdi Rahim$^a$$^b$, Bertrand Thirion$^a$$^b$, Ga\"el Varoquaux$^a$$^b$\\
\end{center}

\begin{center}
{\small \em $^a$Parietal Team, INRIA, Paris-Saclay
University, France.}\\
{\small \em $^b$CEA, DSV, I$^{2}$BM, Neurospin Center,
Paris-Saclay University, 91191, Gif-sur-Yvette, France.}\\
\end{center}

% Here is the abstract.
\begin{abstract}
	Psychiatry and psychology are based on assessing individuals traits,
    characterized through behavioral testing and questionnaires. Imaging of
    brain activity raises the hope of measuring the physiological differences
    that underlie these psychological variations \cite{smith} \cite{miller}. In
    \cite{abraham}, we have
    introduced an automated pipeline capable of learning this link across
    individuals using large cohorts of functional magnetic resonance images
    acquired during rest (Rest fMRI). We present an openly available
    implementation of this pipeline and how we used it to draw best practices
    from its application on various problems. Rest fMRI is a promising
    universal marker of brain function \cite{bharat}, as it can easily be acquired on
    many different individuals and is applicable to disease populations. It is
    used to capture functional-connectivity information, i.e. interaction
    patterns in brain activity. The challenge is then to relate it to behavior
    and pathology. Our pipeline successively defines regions from rest fMRI,
    build connectomes from time series signals extracted upon on these regions
    of interests, and compares connectomes across subjects using machine
    learning. We applied it on five datasets to i) determine the steps to
    obtain the best prediction, and ii) predict phenotypic information with
    good accuracy. Through systematic comparisons, we outline dominant choices
    for each pipeline step. Our results show that this analysis pipeline can
    be adapted to various psychological questions for instance in
    epidemiological studies \cite{miller}, moving imaging closer to a diagnosis tools in
    clinical settings.

%    [1] Smith, Stephen et al. A positive-negative mode of population
%    covariation links brain connectivity, demographics and behavior. Nature
%    Neuroscience, 2015.

%    [2] Miller Karla et al. Multimodal population brain imaging in the UK
%    Biobank prospective epidemiological study. Nature Neuroscience, 2016.

%    [3] Bharat Biswal et al. Toward discovery science of human brain function.
%    PNAS, 2010.
%    [4] Alexandre Abraham et al. Deriving reproducible biomarkers from
%    multi-site resting-state data: An Autism-based example. NeuroImage, 2016.

\end{abstract}
%----
\begin{thebibliography}{9}
    \bibitem{smith} 
        Smith, Stephen et al. 
        \textit{A positive-negative mode of population covariation links brain
        connectivity, demographics and behavior}. 
        Nature Neuroscience, 2015.

    \bibitem{miller} 
        Miller Karla et al. 
        \textit{{Multimodal population brain imaging in the UK Biobank prospective
    epidemiological study}}. Nature Neuroscience, 2016.

    \bibitem{bharat} 
        Bharat Biswal et al.
        \textit{Toward discovery science of human brain function}.
        Proceedings of the National Academy of Sciences, 2010.

    \bibitem{abraham} 
        Alexandre Abraham et al.
        \textit{Deriving reproducible biomarkers from multi-site
        resting-state data: An Autism-based example}.
        Neuroimage, 2016.
\end{thebibliography}
\end{document}

### 2017-06-12 rs_study/experiments/paper/paper.tex
Figures: plot distribution difference on regions and networks
Reorganized prediction scores learned using ICA on COBRE

@@
 \journal{NeuroImage}
-\title{Towards a better predictive model of rest fMRI: benchmarks across
+\title{Towards a better predictive model from rest fMRI: benchmarks across
 multiple phenotypes}
@@
 
-% Start positive
-
-% Introduce cross-validation
-% State the problem
-% Explain what I do, and our conclusion
-
-% XXX: TODO: announce the content of the paper
-
 \section{Methods}
 
-\subsection{Overview of the pipeline}
-\autoref{fig:pipeline}  depicts  our  prediction  pipeline.  It  consists  of  four
-steps: i) Definition  of  brain  regions  of  interest  (ROIs),
-ii) Extraction  of  the  time  series  associated  with  these  ROIs,
-iii) Estimation  of  FC  metrics  from  these  time  series,
-iv) Connectivity-based classification of the phenotypic target.
-\subsection{Definition of brain regions or networks}
+%\subsection{Resting State fMRI (rs-fMRI) prediction pipeline}
+\autoref{fig:pipeline}  depicts  our  prediction  pipeline consists of
+defining brain ROIs, connectivity parameterization and classification using
+machine learning. We used this pipeline to study the various choices
+at each
+step by measuring the impact of each choice made across diverse prediction
+tasks from five different rs-fMRI datasets. In below sections, we outline
+about the choices used at each step, rs-fMRI datasets with the prediction task
+in each dataset and cross-validation framework to prediction accuracy.
+
+%trategy where at step i), we defined brain ROIs from training set of
+%rs-fMRI images where the same set is used for training a linear
+%model classifier in prediction tasks at step iii).
+\subsection{Definition of brain regions of interest (ROIs)}
+There exists many different approaches to define brain ROIs as overviewed
+in \cite{thirion2014}. Here, we choose to
+define brain ROIs using pre-defined brain atlases based on
+anatomical and functional and using data-driven methods. For each type of
+defining brain ROIs, we chose six variety of various
+choices out of which three
+pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
+- Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
+methods - Linear decomposition models: Group Independent Component
+Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
+Clustering models: KMeans - Agglomerative with Ward criterion. For each
+data-driven method, we build the atlas on training data ($75\%$) on each
+split (n=100) and use this atlas for the consecutive step.
 
@@
 
-%begin{figure*}[t]
-%   \setlength{\fboxsep}{0pt}%
-%   \begin{minipage}[T]{.26\paperwidth}
-%    \includegraphics[height=.28\paperwidth]{pipeline.pdf}%
-%    \llap{\raisebox{.265\paperwidth}{%
-%   \parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
-%   \hspace*{-.15ex}\,\hspace{-2ex}}}}}%
-%   \medskip
-%   \end{minipage}
-%   \caption{\textbf{Resting-state functional connectivity prediction pipeline}}
-%
-%   {\bfseries\sffamily 1} -- Defining Brain ROIs: involves using three
-%   pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
-%   - Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
-%   methods - Linear decomposition models: Group Independent Component
-%   Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
-%   Clustering models: KMeans - Agglomerative with Ward criterion. For each
-%   data-driven method, we build the atlas on training data ($75\%$) on each
-%   split (n=100) and use this atlas for the consecutive step. 
-%   %
+\begin{figure*}[tb]
+   \setlength{\fboxsep}{0pt}%
+   \begin{minipage}[T]{.26\paperwidth}
+    \includegraphics[height=.14\paperwidth]{figures/pipeline.pdf}%
+    \llap{\raisebox{.11\paperwidth}{%
+   \parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
+   \hspace*{-.15ex}\,\hspace{-2ex}}}}}%
+   \medskip
+   \end{minipage}
+   \caption{\textbf{Resting-state functional connectivity prediction pipeline}
+   Overview of the pipeline. Pipeline consists of three main steps:
+   {\bfseries\sffamily 1}) defines brain regions (ROIs) from
+   rs-fMRI images or using already defined reference atlases,
+   {\bfseries\sffamily 2}) builds
+   connectomes from time series signals extracted from these ROIs
+   and {\bfseries\sffamily 3}) compares connectomes across subjects using supervised learning.
+   The term connectome is referred to functional connectivity matrix between
+   set of brain ROIs. In other words, we call this pipeline as connectome
+   based prediction pipeline.}
+
   % {\bfseries\sffamily 2} -- Timeseries signal extraction: For each atlas or
@@
   % are Receiver Operating Characteristic and Area Under the Curve (ROC-AUC)
-%   \label{fig:pipeline}
-%end{figure*}
+   \label{fig:pipeline}
+\end{figure*}
 %
@@
     \centerline{%
-	\includegraphics[width=1.\linewidth]{figures/regions_nonregions_difference_distribution.pdf}%
+	\includegraphics[width=1.\linewidth]{figures/regions_networks_difference_distribution.pdf}%
     }%

### 2017-06-13 rs_study/experiments/paper/paper.tex
Update scores with Ward dim=100, 150 on ABIDE

@@
 %\subsection{Resting State fMRI (rs-fMRI) prediction pipeline}
-\autoref{fig:pipeline}  depicts  our  prediction  pipeline consists of
-defining brain ROIs, connectivity parameterization and classification using
-machine learning. We used this pipeline to study the various choices
-at each
-step by measuring the impact of each choice made across diverse prediction
-tasks from five different rs-fMRI datasets. In below sections, we outline
-about the choices used at each step, rs-fMRI datasets with the prediction task
-in each dataset and cross-validation framework to prediction accuracy.
+\autoref{fig:pipeline}  depicts  our  functional-connectivity based
+prediction  pipeline and consists of
+i) defining brain ROIs and extraction of timeseries signals with these
+ROIs, ii) connectivity parameterization between pair of ROIs and
+iii) connectivity-based classification of phenotypic target using
+machine learning.
+We rely on this pipeline to study the various choices at each
+step in the pipeline by measuring the impact of each choice
+made across diverse phenotypic targets from five different
+rs-fMRI datasets.
+
+In below sections, we describe about the methods used at each step
+in the pipeline, rs-fMRI datasets and the phenotypic target used
+within each dataset and cross-validation framework to reporting
+prediction accuracy scores.
 
@@
 \subsection{Definition of brain regions of interest (ROIs)}
-There exists many different approaches to define brain ROIs as overviewed
-in \cite{thirion2014}. Here, we choose to
-define brain ROIs using pre-defined brain atlases based on
-anatomical and functional and using data-driven methods. For each type of
-defining brain ROIs, we chose six variety of various
-choices out of which three
+The first step of the pipeline consists in reducing the
+dimensionality of the problem by aggregating whole brain voxels into
+set of voxels forming a brain ROIs. Each ROI represents a meaningful structure
+of the whole brain where we can use this structure to learn the connectivity
+interactions to study the classification of phenotypic targets, for instance.
+There exists many different kinds of approaches to define brain ROIs
+as overviewed in \cite{thirion2014}. We choose to define brain ROIs
+using two specific approaches. One approach is using reference atlases
+where ROIs are pre-defined while the another approach is
+using data-driven methods where ROIs are defined by directly learning
+on the data. For each approach, we used various choices in
+reference atlases and data-driven methods to study the impact of each
+choice in the prediction pipeline on diverse phenotypic targets. The
+question underlying atlas selection is whether different brain
+disorders lead to a consistent choice, and whether genericity
+should be preferred to adaptative strategies.
+
+generated on another anatomical and functional datasets which are not
+included in this study. Another approach is using
+data-driven methods where ROIs are defined by directly learning on the
+data. For each approach, we used various
+choices to study the impact of each approach in the prediction pipeline on
+diverse prediction tasks.
+
+We outline here various choices used, out of which three are
 pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
-- Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
+- Bootstrap Analysis of Stable Clusters (BASC) and four data-driven
 methods - Linear decomposition models: Group Independent Component
@@
 Clustering models: KMeans - Agglomerative with Ward criterion. For each
-data-driven method, we build the atlas on training data ($75\%$) on each
-split (n=100) and use this atlas for the consecutive step.
+data-driven method, we learn ROIs on training set of rs-fMRI images
+and
 

### 2017-06-15 rs_study/experiments/paper/paper.tex
Writing Methods part for paper

--- 2017-06-12 rs_study/experiments/paper/paper.tex
@@
 %\subsection{Resting State fMRI (rs-fMRI) prediction pipeline}
-\autoref{fig:pipeline}  depicts  our  prediction  pipeline consists of
-defining brain ROIs, connectivity parameterization and classification using
-machine learning. We used this pipeline to study the various choices
-at each
-step by measuring the impact of each choice made across diverse prediction
-tasks from five different rs-fMRI datasets. In below sections, we outline
-about the choices used at each step, rs-fMRI datasets with the prediction task
-in each dataset and cross-validation framework to prediction accuracy.
+\autoref{fig:pipeline}  depicts  our  functional-connectivity based
+prediction  pipeline \citep{abraham2017deriving} and consists of
+following steps: i) defining brain ROIs and extraction of timeseries
+signals from these ROIs,
+ii) connectivity parameterization between pair of ROIs and
+iii) connectivity-based classification of phenotypic target using
+machine learning.
+We study various methods at each
+step in the pipeline by measuring the impact of each method
+made in predicting diverse phenotypic targets across five different
+rs-fMRI datasets.
 
+In below sections, we describe about the methods used at each step
+in the pipeline, rs-fMRI datasets and the phenotypic target used
+within each dataset and cross-validation framework to reporting
+prediction accuracy scores.
+
+As the methods used in the pipeline are well known therefore explaining the
+technical details is out of reach in this paper. The main intention here is to
+tell how we used the methods rather than what each method is.
 %trategy where at step i), we defined brain ROIs from training set of
@@
 \subsection{Definition of brain regions of interest (ROIs)}
-There exists many different approaches to define brain ROIs as overviewed
-in \cite{thirion2014}. Here, we choose to
-define brain ROIs using pre-defined brain atlases based on
-anatomical and functional and using data-driven methods. For each type of
-defining brain ROIs, we chose six variety of various
-choices out of which three
-pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
-- Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
-methods - Linear decomposition models: Group Independent Component
-Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
-Clustering models: KMeans - Agglomerative with Ward criterion. For each
-data-driven method, we build the atlas on training data ($75\%$) on each
-split (n=100) and use this atlas for the consecutive step.
+The first step of the pipeline consists in reducing the
+dimensionality of the problem by aggregating whole brain voxels into
+each set of voxels forming a brain ROIs. Each ROI has a meaningful structure
+underlying in it where we can use this structure to learn the connectivity
+interactions to study the classification of phenotypic targets.
+There exists many different kinds of approaches to define brain ROIs
+as overviewed in \citep{thirion2014}. We choose to define brain ROIs
+using two specific approaches. One approach is using reference atlases
+where ROIs are pre-defined while the another approach is
+using data-driven methods where ROIs are defined by directly learning
+on the data in a \textbf{multi-subject level}. For each approach, we used
+various choices in reference atlases and data-driven methods to study the
+impact of each choice in the prediction pipeline on diverse phenotypic targets.
+The question underlying ROIs selection is whether different brain
+disorders lead to a consistent choice, and whether genericity
+should be preferred to adaptative strategies.
+
+\paragraph{Choices of pre-defined atlases}
+We considered three reference atlases: i) \textbf{Automated Anatomical Labeling
+(AAL)} \citep{tzourio-mazoyer2002a}, a structural atlas obtained on
+unseen single-subject high-resolution T1 image of 116 ROIs,
+ii) \textbf{Harvard Oxford}
+\citep{desikan2006}, a probabilistic cortical segmented structural
+atlas learned on unseen 40 subjects T1 images, contains of 48 ROIs in
+each hemisphere of total 96 ROIs. iii) \textbf{Bootstrap Analysis of
+Stable Clusters (BASC)} \citep{bellec2010}, a multi scale functional atlas
+extracted using K-Means clustering on rs-fMRI dataset which
+consists of 43 healthy subjects. We considered exploring various scales set
+in $\{036, 064, 122, 197, 325, 444\}$.
+
+\paragraph{Choices of data-driven atlases}
+We considered four popular data exploratory methods most widely used in the
+fMRI community to learn the functional connectivity of the human brain driven
+by intrinsic activity from these ROIs \citep{yeo2011, kahnt2012, thirion2014}
+\citep{calhoun2001a, beckmann2004, varoquaux2011, abraham2013}.
+Inspired from these research methods, we choose to build brain
+atlases from multi-subject rs-fMRI images using \textbf{two clustering
+methods} mainly:
+i) \textbf{K-Means} \citep{sculley2010}, and ii) hierarchical agglomerative
+clustering using \textbf{Ward’s algorithm} \citep{ward1963} added with
+spatial connectivity matrix to map together all neighboring voxels sharing
+the same information, and \textbf{two
+are data decomposition linear methods} where these two methods have quite
+different approach in extraction of brain ROIs, namely: iii) \textbf{
+Canonical Independent Component Analysis (GroupICA) or (CanICA)}
+\citep{varoquaux2010}, iv) \textbf{Online Dictionary Learning
+(DictLearn)} \citep{mensch2016}.
+
+\paragraph{Choices of dimensionalities and dimensionality reduction}
+Prior to defining brain ROIs with clustering methods
+i.e., K-Means and Ward, we reduced the dimensionality
+of the multi-subject rs-fMRI images in a group level using Principal Component
+Analysis (PCA) \citep{smith2014} to $n=100$ components.
+Given these PCA components, we define the brain ROIs with
+varying in cluster dimensions in $dim=\{40, 60, 80, 100, 120, 150, 200, 300\}$
+where our intention also lies in studying the
+impact of dimensionality in building brain ROIs used for prediction of
+diverse phenotypic targets.
+
+While with data decomposition methods i.e., CanICA and DictLearn,
+we vary the dimensionality reduction components $n$
+according to brain ROIs defining dimensions in $dim=\{40, 60, 80, 100, 120,
+150\}$\footnote{For less ambiguity, we focussed to report results with less
+    dimensions especially for CanICA and DictLearn where the computational
+    cost is high in defining brain ROIs. However, we also investigated
+for higher dimensions in $dim=\{200, 300\}$ without any improvements in the
+results}.
+We share almost common parameters across each pair of data-driven methods
+to compare them efficiently between clustering methods or
+between data decomposition methods. Also, all data-driven methods altogether.
+
+For each data-driven method, we
+learn brain ROIs on training set of rs-fMRI images to overcome overfitting
+results \citep{abraham2017deriving}.
+The ratio of training set used to learn brain ROIs is described below in section
+Experimental study. We also used Gaussian smoothing on rs-fMRI images
+with Full Width Half Maximum (FWHM) of $6mm$ for all
+data-driven methods prior to learning brain ROIs. We used common smoothing to
+avoid possible variance with the definition of ROIs which may arise while
+varying the smoothness on the rs-fMRI images.
+
+\paragraph{Choices of regions or networks}
+While defining brain ROIs, we are also interested to study the
+impact on the prediction driven by brain ROIs defined with either regions
+or networks. Regions implies separating the
+biggest connected components or networks in the brain extracted to independent
+regions which are
+spatially contiguous \citep{abraham2014region}. For example, separating
+bi-hemispheric brain network to regions onto each hemisphere or separating default
+mode network (DMN) to each a independent region.
+Whereas networks implies using directly as it is without implying any regions
+method.
+
+We used a Random Walker segmentation approach to extract regions in the
+brain networks decomposed by methods in CanICA and DictLearn as proposed in
+\citep{abraham2014region}. While for BASC and K-Means, we used simple
+label\footnote{For label reassignment approach, we used multidimensional
+module named as ndimage.label from scipy software.}
+reassignment approach to extract the biggest connected components to regions
+assigned with new label. In particular we compare in regions or networks with
+all methods except AAL, Harvard Oxford and Ward.
+During this procedure, we remove
+spurious regions of size $< 1500 mm^{3}$. An example of the brain atlases obtained
+through data-driven methods on ADNI rs-fMRI dataset is presented in
+\autoref{fig:brain_rois}.
+
+\paragraph{Time-series signals extraction}
+After definition of brain ROIs, we extract a representative time-series
+for each ROI in each subject. For atlases composed of non-overlapping
+ROIs as can be seen in \autoref{fig:brain_rois} (bottom row), we simply
+compute the weighted average of the fMRI
+time series signals over all voxels within that specific region.
+For fuzzy overlapping ROIs, such as the components extracted
+by CanICA and DictLearn as shown in \autoref{fig:brain_rois} (top row),
+we use a linear model to unmix the
+signal in each voxel as the additive decomposition of signals
+over several overlapping ROIs.
+
+Standard pre-processing steps are applied on a signal extraction level
+to regress out confounds or nuisance signals. We extracted $10$ CompCor
+high-variance confounds on the whole brain using similar method as
+proposed in \citep{behzadi2007} and also used $6$ motion confounds pre-extracted
+during motion realignment in $6$ directions while pre-processing raw rs-fMRI
+images\footnote{\url{https://github.com/neurospin/pypreprocess}}.
+We have not used any motion
+confounds for ABIDE \citep{dimartino2014autism} and
+ACPI\footnote{\url{http://fcon_1000.projects.nitrc.org/indi/ACPI/html/}}
+rs-fMRI images as the data is already
+pre-processed using standard preprocessed initiative protocols.
+More details on pre-processing steps used for raw rs-fMRI
+images can be in Section Experimental study.
+The signal of each region is also
+then normalized, detrended and bandpass-filtered between 0.01
+and 0.1 Hz. The primary motivation using pre-processing on a signal extraction
+level is to reject non-neural information i.e., information corresponding to
+acquisition noise or cardiac activity or physiological random noise and get
+cleaned timeseries as much as possible to learn the functional-connectivity
+interactions which are crucial for classification step in supervised learning
+as proposed in \citep{varoquaux2013connectomes}.
 
@@
     \centerline{%
-	\includegraphics[width=0.5\paperwidth]{figures/brainrois.pdf}%
+	\includegraphics[width=1.2\linewidth]{figures/rois2.pdf}%
     }%
     \caption{\textbf{Brain regions/parcellations using ICA, DictLearn, KMeans,
-        Ward}
+        Ward} Brain atlas with Dictionary Learning is chosen with
+        $n=60$ resting state networks separated to regions whereas same with
+        ICA but $n=80$ resting state networks. For KMeans and Ward, brain
+        parcellations are chosen for $n=120$ dimensions.
     %
@@
 
-\section{Discussion:}
+\section{Discussion}
 
@@
 
-\section{Conclusion:}
+\section{Conclusion}
 
@@
 
-\section{Supplementary material}
+\section{References}
+\small
 %\bibliographystyle{elsarticle-num-names}

### 2017-06-15 submissions/ohbm_2017/Poster/poster.tex
Poster of OHBM 2017

\documentclass[portrait,a0,final]{a0poster} % a0poster class sets the paper size
\usepackage[RGB,A0]{ScientificPosterTemplate} % RGB, Coated, Uncoated
\usepackage[english]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf} % so that ''pdflatex'' accepts .eps files
\usepackage{titlesec} % For changing the font on chapters, sections, etc.
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{tabularx}
\usepackage{lipsum} % Lorem ipsum generator
\usepackage{floatrow}

\definecolor{bleu}{RGB}{0,140,189}%

%% Section font size reduction for a0 posters %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \titleformat{\section}{\large\bfseries\sffamily\color{posterBlack}}{\textcolor{posterBlack}{\thesection}}{1em}{} % Text size for a1 posters
% \titleformat{\section}{\large\bfseries\sffamily}{\thesection.}{1em}{} % Text size for a1 posters with a dot after the incremental number
\titleformat{\section}{\huge\bfseries\sffamily\color{bleu}}{\textcolor{bleu}{\thesection.}}{1em}{} % Text size for a1 posters with a dot after the incremental number

%% Safe alternative math font (optional)
% \usepackage{fouriernc}

%% Teach hyphenation for alien words
% \hyphenation{op-tical net-works semi-conduc-tor}

%% Font sizes for a0poster are
%\tiny
%\scriptsize
%\footnotesize
%\small
%\normalsize
%\large
%\Large
%\LARGE
%\huge
%\Huge
%\veryHuge
%\VeryHuge
%\VERYHuge

%% Colors from ScientificPosterTemplate-package
% posterBlack
% posterGray
% posterYellow
% posterOrange
% posterRed
% posterFuchsia
% posterPurple
% posterBlue
% posterTurquoise
% posterGreen
% posterLightGreen
% You can use \textcolor{<posterColor>}{<your text>) to change the colors of text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\thispagestyle{empty} % Removes the page number

\begin{minipage}[t]{0.98\linewidth} % The first minipage for the logo & title
\vspace{0pt} % A trick to align the parallel minipages on top

\vspace{0.008\linewidth} % Increase the top margin

\begin{minipage}[t]{0.95\linewidth} % title
\vspace{0pt} % Alingns the parallel minipages on top

%% Title: use \baselinestretch to change linespacing, \textit{} for italic text, \textcolor for colored text
% More conservative title, upright and black
{\renewcommand{\baselinestretch}{0.85} % Changes the baseline skip smaller for the title
\VeryHuge{\bfseries{\textsf{\textcolor{bleu}{Towards a better predictive model
from rest fMRI: benchmarks across multiple phenotypes}}}} % Text size for a1 posters
\par} % <- for \baselinestretch

\vspace{0.02\linewidth} % Empty space after the title

\Large{\textsf{\bfseries{\underline{Kamalaker Dadi}$^{1*}$, Darya Chyzhyk$^1$,
Alexandre Abraham$^1$, Mehdi Rahim$^1$, Bertrand Thirion$^1$,
Gael Varoquaux$^1$}}} % Text size for a1 posters

\vspace{0.01\linewidth}
\Large{\textcolor{posterBlack}{\textsf{%\bfseries{
            $^1$Parietal team, Neurospin -- I${^2}$BM -- CEA, INRIA, Paris-Saclay, France \\ $^*$kamalaker-reddy.dadi@inria.fr%}
}}}
%
\end{minipage}
\hspace{0.08\linewidth}
%\begin{minipage}{0.15\linewidth} % logo
%\vspace{0pt} % Alingns the parallel minipages on top
%\begin{flushright}
%\includegraphics[width=0.30\linewidth,
%angle=0]{figures/logos/parietal_web_page.png}
%\end{flushright}

%\end{minipage} % no empty line before the next begin

\end{minipage}

%% Two columns

% Space according to the visual identity guidelines...
\vspace{0.04\linewidth}

% Centering helps in placement
\centering
\Large % Text size for a1 posters
\sffamily % font sans serif

\begin{minipage}{0.98\linewidth}

\begin{minipage}[t]{0.48\linewidth}
\setlength{\parindent}{10mm} % Paragraph indent

\section{Introduction}
Psychiatry and psychology are based on assessing individuals traits,
characterized through
behavioral testing and questionnaires. Imaging of brain activity raises the
hope of measuring
the physiological differences that underlie these psychological variations
\cite{miller}. In \cite{abraham}, we have
introduced an automated pipeline capable of learning this link across
individuals using large
cohorts of functional magnetic resonance images acquired during rest (Rest
fMRI). We present the outline of this pipeline
and how we used it to draw best practices from its application on various problems.

\vspace{0.8\sectionspace}
\section{A connectome classification pipeline}
We applied the pipeline on five datasets to i) determine the steps to obtain
the best
prediction, and ii) predict phenotypic information with good accuracy.

%\vspace{\figurespace}
\begin{center}
\includegraphics[width=1\linewidth]{figures/functional_connectivity_pipeline.pdf}
\end{center}
\captionof{figure}{\textbf{Our pipeline consists of three main steps}: defines regions
    from rest fMRI,
    builds connectomes from time series signals extracted from these
    regions of interests, and compares connectomes across subjects using
machine learning. \label{fig_1}}
%\vspace{\figurespace}

\vspace{0.6\sectionspace}
\section{Rest fMRI datasets}

\begin{center}
    \begin{tabular}{ccc}
        \rowcolor{gray!50}
        Dataset & Subjects & Clinical question \\
        \hline\\[-4mm]
        COBRE & $65/77$ & Schizophrenia vs Control \\
        \rowcolor{gray!13}
        ADNI & $40/96$ & AD vs MCI  \\
        ADNIDOD & $89/78$& PTSD vs Control \\
        \rowcolor{gray!13}
        ACPI & $62/64$ & Marijuana use vs Control \\
        ABIDE & $402/464$ & Autism vs Control
    \end{tabular}
\end{center}
\captionof{table}{Description of the five rs-fMRI
    datasets used.
    AD - Alzheimer's Disease, MCI - Mild
    Cognitive Impairment,
    PTSD - Post Traumatic Stress Disorder.}
%\vspace{\tablespace}

\section{Pipelining choices}
    %\begin{enumerate}
    %   \item Defining Brain ROIs
    %   \item Connectivity parameterizing
    %   \item Supervised Learning: Classifiers
    %\end{enumerate}
%\vspace{\figurespace}
\begin{center}
\includegraphics[width=0.7\linewidth]{figures/only_pipeline_choices.pdf}
\end{center}
\captionof{figure}{{\bfseries\sffamily 1 -- Defining Brain ROIs} can be done using
    three pre-defined atlases: two anatomical - Automated Anatomical Labeling
    (AAL), Harvard Oxford and one functional - Bootstrap Analysis
    of Stable Clusters (BASC). Four region learning methods: two Linear
    decomposition models - Group Independent Component Analysis (Group ICA),
    Online Dictionary Learning and two Clustering models - KMeans,
    Agglomerative with Ward criterion.
    {\bfseries\sffamily 2 -- Parameterizing functional connectivity
    between ROIs}: correlation, partial correlation or tangent space embedding
    {\bfseries\sffamily 3 -- Supervised learning}: Classifiers, a
classification
    model is built to predict groups with two linear classifiers, SVC
($\ell_{1}$
    or $\ell_{2}$ penalization) and Ridge. Definition of brain regions (below). \label{fig_2}}
%\vspace{\figurespace}

%\begin{centering}
\begin{minipage}{0.22\textwidth}
\begin{minipage}{1.5\linewidth}
\begin{center}
\includegraphics[width=2.22\linewidth]{figures/rois2.pdf}
%\captionof{figure}{Definition of Brain regions. \label{fig_3}}
\end{center}
\end{minipage}
\end{minipage}
%\end{centering}
%\vspace{\figurespace}
%\begin{minipage}[t]{0.35\linewidth}
%        Here is the text
%          \end{minipage}\hfill
%            \begin{minipage}[b]{0.55\linewidth}
%                    \includegraphics[width=40cm]{figures/rois.pdf}
%                        \captionof{figure}{A wonderful picture}
%                          \end{minipage}
%

% The end of the first column and the start of the second
\end{minipage} % no empty line before the next ''\begin''
\hspace{0.02\linewidth} % Middle margin
\begin{minipage}[t]{0.48\linewidth}
\setlength{\parindent}{10mm} % Paragraph indent

\section{Results}
\subsection{Prediction scores in AUC}
\begin{tabularx}{\textwidth}{p{7.5cm}|p{5.5cm}|p{5.5cm}|p{5.5cm}|p{5.5cm}|p{5.5cm}}
    \rowcolor{gray!50}
    \centering{Accuracy} & \centering{COBRE} & \centering{ADNI} &
    \centering{ADNIDOD} & \centering{ACPI} & ABIDE \\
    \hline
    \rowcolor{gray!13}
    \centering{Median}& \centering{$87.1\%$} & \centering{$76.2\%$} &
    \centering{$67.1\%$} & \centering{$56.4\%$} & $70.2\%$\\
    % \rowcolor{gray!13}%
        {\centering $5^{th}$ Percentile} & \centering{$74.3\%$} &
    \centering{$62.3\%$} & \centering{$53.8\%$} & \centering{$41.4\%$} & $64.9\%$\\
    \rowcolor{gray!13}
    {\centering $95^{th}$ Percentile} & \centering{$94\%$} &
    \centering{$89.1\%$} & \centering{$77.2\%$} & \centering{$68.7\%$} & $73.8\%$\\
    \hline
\end{tabularx}
\captionof{table}{\textbf{Median, 5th percentile and 95th percentile of
        accuracy scores in AUC over cross-validation folds ($n=100$) across
        multi rs-fMRI datasets.} Functional brain atlases learned using Online
        Dictionary Learning\cite{arthur} with $60$ resting state networks
        and spliting networks to regions are used in the prediction pipeline
        with Tangent based connectivity matrix parameterization\cite{varoquaux} and
        Support Vector Classifier with $\ell{_2}$ penalization (SVC-$\ell{_2}$).}

\subsection{Choice of classifier, connectivity and brain atlas}
%\vspace{\figurespace}
\begin{center}
\begin{minipage}[t]{0.48\linewidth}
\begin{center}
\includegraphics[width=0.95\linewidth]{figures/impact_plot_classifier.pdf}\\\normalsize
(a) classifier
\end{center}
\end{minipage}
\hspace{0.02\linewidth} % Middle margin
\begin{minipage}[t]{0.48\linewidth}
\begin{center}
\includegraphics[width=0.87\linewidth]{figures/impact_plot_measure.pdf}\\\normalsize
(b) connectivity parameterization
\end{center}
\end{minipage}
\end{center}
%\captionof{figure}{The impact of classifier (a), connectivity
%parameterization (b)
%            choices in functional connectivity prediction pipeline over
%                    diverse tasks. \label{fig_3}}
%\vspace{\figurespace}

%\subsection{Choice of atlas}
%\vspace{\figurespace}
\begin{minipage}[t]{0.98\textwidth}
\begin{center}
\includegraphics[width=0.8\linewidth]{figures/impact_plot_atlas.pdf}\\
\normalsize (c) brain atlases with optimal choices in dimensionality
-- BASC (122 networks to regions) -- Ward (120) --
K-Means (120 parcellations) --
GroupICA (80 networks to regions) -- DictLearn (60 networks to regions)
%\vspace{\figurespace}
\end{center}
\end{minipage}
\captionof{figure}{The \textbf{impact of choices} in functional connectivity prediction
    pipeline over diverse tasks.
    (*) indicates the optimal option.
        \label{fig_3}}

%\vspace{\sectionspace}
\section{Optimal choices}
\begin{itemize}
    %\item Functional-Connectivity based pipeline across diverse clinical targets
    \item Systematic exploration of choices at each step
    \item Definition of Brain ROIs - Linear Decomposition models
    \item Connectivity Parameterization - Tangent Space Embedding
    \item Classification with Support Vector Classifier - $\ell{_2}$
        penalization.
\end{itemize}

\nocite{*}
%\vspace{\sectionspace}
\begin{spacing}{0.6}
\bibliographystyle{naturemag}
\bibliography{references}
\end{spacing}

\end{minipage}
\end{minipage} % minipage for the two columns (minipages)

\vfill % Fill the free space until the footer minipages

\begin{minipage}{0.98\textwidth} % Minipages for the footers

\large % Text size for footers

\begin{minipage}[c]{0.475\linewidth}% Footer #1
\vspace{0pt}
\begin{center}
\textcolor{posterGray}{\hrule}
\vspace{0pt}
\includegraphics[height=17mm, angle=0]{figures/logos/parietal_web_page.png}
\qquad \quad
\includegraphics[height=17mm, angle=0]{figures/logos/neurospin.jpg}
\qquad \quad
\includegraphics[height=29mm, angle=0]{figures/logos/logo-inria2.jpg}
\end{center}
\end{minipage} % No empty line before the second begin!
\hspace{0.01\linewidth}
\begin{minipage}[c]{0.575\linewidth} % Footer #2
    \begin{center}
\vspace{0pt}
\textbf{\sffamily Acknowledgments:}\\
ANR-11-BINF-0004\_NiConnect and
CATI project.
\end{center}
\end{minipage}

\end{minipage}

\vspace*{0.03\linewidth} % Increase the bottom margins

\end{document}

### 2017-06-24 submissions/ohbm_2017/Poster/poster.tex
Big picture plots

@@
+\pdfminorversion=4
 \documentclass[portrait,a0,final]{a0poster} % a0poster class sets the paper size
@@
 % More conservative title, upright and black
-{\renewcommand{\baselinestretch}{0.85} % Changes the baseline skip smaller for the title
-\VeryHuge{\bfseries{\textsf{\textcolor{bleu}{Towards a better predictive model
-from rest fMRI: benchmarks across multiple phenotypes}}}} % Text size for a1 posters
+{\renewcommand{\baselinestretch}{0.8} % Changes the baseline skip smaller for the title
+\VeryHuge{\bfseries{\textsf{\textcolor{bleu}{Predictive models based on
+functional connectivity: a benchmark across multiple datasets}}}} % Text size for a1 posters
 \par} % <- for \baselinestretch
@@
 
-\Large{\textsf{\bfseries{\underline{Kamalaker Dadi}$^{1*}$, Darya Chyzhyk$^1$,
-Alexandre Abraham$^1$, Mehdi Rahim$^1$, Bertrand Thirion$^1$,
-Gael Varoquaux$^1$}}} % Text size for a1 posters
+\Large{\textsf{\bfseries{Kamalaker DADI$^{1}$, Alexandre ABRAHAM$^1$,
+Mehdi RAHIM$^1$, Darya CHYZHYK$^1$, Bertrand THIRION$^1$,
+Ga{\"e}l VAROQUAUX$^1$}}} % Text size for a1 posters
 
@@
 \Large{\textcolor{posterBlack}{\textsf{%\bfseries{
-            $^1$Parietal team, Neurospin -- I${^2}$BM -- CEA, INRIA, Paris-Saclay, France \\ $^*$kamalaker-reddy.dadi@inria.fr%}
+            $^1$Parietal team, Neurospin -- CEA, INRIA, Paris-Saclay, France%}
 }}}
@@
 \end{minipage}
-\hspace{0.08\linewidth}
-%\begin{minipage}{0.15\linewidth} % logo
+\begin{minipage}{0.76\paperwidth}
+\vspace{-0.035\linewidth}
+\begin{flushright}
+\includegraphics[height=15mm, angle=0]{figures/logos/parietal_web_page.png}
+\qquad \quad
+\includegraphics[height=15mm, angle=0]{figures/logos/neurospin.jpg}
+\qquad \quad
+\includegraphics[height=26mm, angle=0]{figures/logos/logo-inria2.jpg}
+\end{flushright}
+\end{minipage} % No empty line before the second begin!
+%\hspace{0.01\linewidth}
+%\begin{minipage}{0.95\linewidth} % logo
+%    \hfill
 %\vspace{0pt} % Alingns the parallel minipages on top
 %\begin{flushright}
-%\includegraphics[width=0.30\linewidth,
+%\includegraphics[width=0.20\linewidth,
 %angle=0]{figures/logos/parietal_web_page.png}
@@
 % Space according to the visual identity guidelines...
-\vspace{0.04\linewidth}
+\vspace{0.03\linewidth}
 
@@
 \section{Introduction}
-Psychiatry and psychology are based on assessing individuals traits,
-characterized through
-behavioral testing and questionnaires. Imaging of brain activity raises the
-hope of measuring
-the physiological differences that underlie these psychological variations
-\cite{miller}. In \cite{abraham}, we have
-introduced an automated pipeline capable of learning this link across
-individuals using large
-cohorts of functional magnetic resonance images acquired during rest (Rest
-fMRI). We present the outline of this pipeline
-and how we used it to draw best practices from its application on various problems.
+\begin{itemize}
+    \item Psychiatry and psychology are based on assessing individuals traits
+        characterized through \textbf{behavioral testing} and
+        \textbf{questionnaires}.
+    \item \textbf{Imaging of brain activity} measures the physiological
+        differences that underlie these \textbf{psychological
+        variations}\cite{miller}.
+    \item Introduction of \textbf{automated pipeline}\cite{abraham}.
+        \begin{itemize}
+            \item  Learning the \textbf{link} across individuals.
+            \item Large cohorts of functional magnetic resonance images at
+                rest \textbf{(Rest-fMRI)}.
+        \end{itemize}
+    \item We present the \textbf{outline} of this pipeline
+        and how we used it to \textbf{draw best practices} from the
+        application of pipeline on
+        various problems.
+\end{itemize}
 
-\vspace{0.8\sectionspace}
+\vspace{0.3\sectionspace}
 \section{A connectome classification pipeline}
-We applied the pipeline on five datasets to i) determine the steps to obtain
-the best
-prediction, and ii) predict phenotypic information with good accuracy.
+%We applied the pipeline on five datasets to i) determine the steps to obtain
+%the best
+%prediction, and ii) predict phenotypic information with good accuracy.
 
@@
 
-\vspace{0.6\sectionspace}
+\vspace{0.0991\sectionspace}
 \section{Rest fMRI datasets}
@@
 \end{center}
-\captionof{table}{Description of the five rs-fMRI
-    datasets used.
+\captionof{table}{Description of the \textbf{five rs-fMRI
+    datasets} used.
     AD - Alzheimer's Disease, MCI - Mild
@@
 \begin{center}
-\includegraphics[width=0.7\linewidth]{figures/only_pipeline_choices.pdf}
+\includegraphics[width=0.7\linewidth]{figures/only_pipeline_choices2.pdf}
 \end{center}
@@
 %\begin{centering}
-\begin{minipage}{0.22\textwidth}
-\begin{minipage}{1.5\linewidth}
+\begin{minipage}{0.38\linewidth}
 \begin{center}
-\includegraphics[width=2.22\linewidth]{figures/rois2.pdf}
+\includegraphics[width=2.5\linewidth]{figures/rois2.pdf}
 %\captionof{figure}{Definition of Brain regions. \label{fig_3}}
 \end{center}
-\end{minipage}
 \end{minipage}
@@
 
+\begin{spacing}{0.7}
+\begin{minipage}[c]{0.675\linewidth}
+    \begin{center}
+\vspace{0.1\linewidth}
+\textbf{\large Acknowledgments:}\\
+\vspace{0.02\linewidth}
+\large{ANR-11-BINF-0004\_NiConnect and CATI project}.
+%\vspace{0.02\linewidth}
+%\textcolor{posterGray}{\hrule}
+%\vspace{0.02\textwidth}
+%See Also Posters: \textbf{$\#1656$, $\#1829$, $\#3934$}
+\end{center}
+
+\end{minipage}
+\end{spacing}
+
+\begin{minipage}[c]{0.995\linewidth}
+\vspace{0pt}
+\begin{flushright}
+\vspace{-0.03\linewidth}
+\includegraphics[height=64mm, angle=0]{figures/logos/nilearn-logo.png}
+\end{flushright}
+\end{minipage}
+
 \end{minipage}
@@
 
-\begin{minipage}{0.98\textwidth} % Minipages for the footers
+%\begin{minipage}{0.98\textwidth} % Minipages for the footers
 
-\large % Text size for footers
+%\large % Text size for footers
 
-\begin{minipage}[c]{0.475\linewidth}% Footer #1
-\vspace{0pt}
-\begin{center}
-\textcolor{posterGray}{\hrule}
-\vspace{0pt}
-\includegraphics[height=17mm, angle=0]{figures/logos/parietal_web_page.png}
-\qquad \quad
-\includegraphics[height=17mm, angle=0]{figures/logos/neurospin.jpg}
-\qquad \quad
-\includegraphics[height=29mm, angle=0]{figures/logos/logo-inria2.jpg}
-\end{center}
-\end{minipage} % No empty line before the second begin!
-\hspace{0.01\linewidth}
-\begin{minipage}[c]{0.575\linewidth} % Footer #2
-    \begin{center}
-\vspace{0pt}
-\textbf{\sffamily Acknowledgments:}\\
-ANR-11-BINF-0004\_NiConnect and
-CATI project.
-\end{center}
-\end{minipage}
+%\begin{minipage}[c]{0.475\linewidth}% Footer #1
+%\vspace{0pt}
+%\begin{center}
+%\textcolor{posterGray}{\hrule}
+%\vspace{0pt}
+%\includegraphics[height=17mm, angle=0]{figures/logos/parietal_web_page.png}
+%\qquad \quad
+%\includegraphics[height=17mm, angle=0]{figures/logos/neurospin.jpg}
+%\qquad \quad
+%\includegraphics[height=29mm, angle=0]{figures/logos/logo-inria2.jpg}
+%\end{center}
+%\end{minipage} % No empty line before the second begin!
+%\hspace{0.01\linewidth}
+%\begin{minipage}[c]{0.575\linewidth} % Footer #2
+%    \begin{center}
+%\vspace{0pt}
+%\textbf{\sffamily Acknowledgments:}\\
+%ANR-11-BINF-0004\_NiConnect and
+%CATI project.
+%\end{center}
+%\end{minipage}
 
-\end{minipage}
+%\end{minipage}
 

### 2017-06-24 rs_study/experiments/plotting_scripts_for_paper/plot_impact_atlas.py

@@ -1,0 +1,347 @@
+
+import pandas as pd
+import os
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import seaborn as sns
+from collections import OrderedDict
+import numpy as np
+
+from my_palette import (color_palette, atlas_palette,
+                        datasets_palette)
+
+
+def stripplot_mean_score(df, save_path, dic_model_dim, suffix=None, x=None,
+                         y=None, hue=None, style='whitegrid', fontsize=14,
+                         jitter=.2, figsize=(9, 3), leg_pos=2,
+                         leg_borderpad=None, leg_ncol=1, leg_bbox_to_anchor=None):
+    marker_dict = {'COBRE': 'o',
+                   'ADNI': 's',
+                   'ADNIDOD': '>',
+                   'ACPI': '^',
+                   'ABIDE': 'v'}
+
+    # make-up the data
+    def change_label_name(row, label):
+        row[label] = new_names[row[label]]
+        return row
+
+    # atlas labels
+    if y == 'atlas':
+        ylabel = "Atlas"
+        #new_names = OrderedDict([('ica', 'ICA \n (' + str(dic_model_dim['ica'])
+        #                          + ' regions)'),
+        #                         ('kmeans', 'K-Means \n (' + str(dic_model_dim['kmeans'])
+        #                          + ' regions)'),
+        #                         ('dictlearn', 'Dictionary \n Learning \n '
+        #                                       '(40 regions)'),
+        #                         ('ward', 'Ward \n (120 regions)'),
+        #                         ('aal_spm12', 'AAL \n (116 regions)'),
+        #                         ('basc', 'BASC \n (122 regions)'),
+        #                         ('harvard_oxford', 'HO \n (96 regions)')])
+
+        new_names = OrderedDict([('ica', 'Group ICA'),
+                                 ('kmeans', 'K-Means'),
+                                 ('dictlearn', 'Online \n Dictionary \n Learning'),
+                                 ('ward', 'Ward'),
+                                 ('aal_spm12', 'AAL'),
+                                 ('basc', 'BASC'),
+                                 ('harvard_oxford', 'Harvard \n Oxford')])
+        df = df.apply(lambda x: change_label_name(x, y), axis=1)
+
[…]

### 2017-06-24 rs_study/experiments/plotting_scripts_for_paper/plot_impact_classifier.py

@@ -1,0 +1,302 @@
+__author__ = 'darya'
+
+import pandas as pd
+import os
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import seaborn as sns
+from collections import OrderedDict
+import numpy as np
+
+from my_palette import (color_palette, atlas_palette,
+                        datasets_palette)
+
+
+def stripplot_mean_score(df, save_path, dic_model_dim, suffix=None, x=None,
+                         y=None, hue=None, style='whitegrid', fontsize=14,
+                         jitter=.2, figsize=(9, 3), leg_pos=2,
+                         leg_borderpad=None, leg_ncol=1, leg_bbox_to_anchor=None):
+    marker_dict = {'COBRE': 'o',
+                   'ADNI': 's',
+                   'ADNIDOD': '>',
+                   'ACPI': '^',
+                   'ABIDE': 'v'}
+
+    # make-up the data
+    def change_label_name(row, label):
+        row[label] = new_names[row[label]]
+        return row
+
+    # classifier labels
+    if y == 'classifier':
+        new_names = {'ridge': 'Ridge',
+                     'svc_l1': r'SVC-$\ell_1$',
+                     'svc_l2': r'SVC-$\ell_2$'}
+        df = df.apply(lambda x: change_label_name(x, y), axis=1)
+
+    # change the name of the dataset to upper
+    df['dataset'] = df['dataset'].str.upper()
+
+    # make labels of the y axes shorter
+    # df[y] = df[y].str.wrap(13)
+
+    rc('xtick', labelsize=12)
+    rc('ytick', labelsize=12)
+    rc('axes', labelweight='bold')  # string.capitalize
+    rc('legend', fontsize=fontsize)
+
+    n_datasets = len(df['dataset'].unique())
+    palette = color_palette(n_datasets)
+
+    fig, axx = plt.subplots(nrows=1, ncols=1, figsize=figsize, sharey=False)
+
+    # draw a default vline at x=0 that spans the yrange
+    axx.axvline(x=0, linewidth=4, zorder=0, color='0.6')
+
+    sns.boxplot(data=df, x=x, y=y, fliersize=0, linewidth=2,
+                boxprops={'facecolor': '0.8', 'edgecolor': '.0'},
+                width=0.8, ax=axx)
+    width_of_boxplot = 0.8
+    offset = width_of_boxplot / n_datasets
[…]

### 2017-06-24 rs_study/experiments/plotting_scripts_for_paper/plot_impact_connectivity_parameterization.py

@@ -1,0 +1,280 @@
+"""
+"""
+import pandas as pd
+import os
+import matplotlib
+import matplotlib.pyplot as plt
+from matplotlib import rc
+import seaborn as sns
+from collections import OrderedDict
+import numpy as np
+
+from my_palette import (color_palette, atlas_palette,
+                        datasets_palette)
+
+
+def stripplot_mean_score(df, save_path, dic_model_dim, suffix=None, x=None,
+                         y=None, hue=None, style='whitegrid', fontsize=14,
+                         jitter=.2, figsize=(9, 3), leg_pos=2,
+                         leg_borderpad=None, leg_ncol=1, leg_bbox_to_anchor=None):
+    marker_dict = {'COBRE': 'o',
+                   'ADNI': 's',
+                   'ADNIDOD': '>',
+                   'ACPI': '^',
+                   'ABIDE': 'v'}
+
+    # make-up the data
+    def change_label_name(row, label):
+        row[label] = new_names[row[label]]
+        return row
+
+    # measure labels
+    if y == 'measure':
+        # ylabel = "Connectivity Parameterization"
+        new_names = {'correlation': 'Correlation',
+                     'partial correlation': 'Partial \n correlation',
+                     'tangent': 'Tangent'}
+        df = df.apply(lambda x: change_label_name(x, y), axis=1)
+
+    # change the name of the dataset to upper
+    df['dataset'] = df['dataset'].str.upper()
+
+    # make labels of the y axes shorter
+    # df[y] = df[y].str.wrap(13)
+
+    rc('xtick', labelsize=12)
+    rc('ytick', labelsize=12)
+    rc('axes', labelweight='bold')  # string.capitalize
+    rc('legend', fontsize=fontsize)
+
+    n_datasets = len(df['dataset'].unique())
+    palette = color_palette(n_datasets)
+
+    fig, axx = plt.subplots(nrows=1, ncols=1, figsize=figsize, sharey=False)
+
+    # draw a default vline at x=0 that spans the yrange
+    axx.axvline(x=0, linewidth=4, zorder=0, color='0.6')
+
+    sns.boxplot(data=df, x=x, y=y, fliersize=0, linewidth=2,
+                boxprops={'facecolor': '0.8', 'edgecolor': '.0'},
+                width=0.8, ax=axx)
+    width_of_boxplot = 0.8
+    offset = width_of_boxplot / n_datasets
+    n_offsets = [-offset * 2, -offset * 1, 0, offset * 1, offset * 2]
+
[…]

### 2017-07-05 rs_study/experiments/plotting_scripts_for_paper/plot_impact_atlas.py
Prediction scores using Ward for dim=[200, 300] on ABIDE

@@ -75,7 +75,7 @@ def stripplot_mean_score(df, save_path, dic_model_dim, suffix=None, x=None,
     axx.axvline(x=0, linewidth=4, zorder=0, color='0.6')
 
     plot = sns.boxplot(data=df, x=x, y=y, fliersize=0, linewidth=2,
-                       boxprops={'facecolor': '0.8', 'edgecolor': '.0'},
+                       boxprops={'facecolor': 'c', 'edgecolor': '.0'},
                        width=0.8, ax=axx)
     width_of_boxplot = 0.8
     offset = width_of_boxplot / n_datasets
